---
title: "MacroEcol_6_ManuscriptStatsSummary"
author: "Laura Ospina-Rozo"
date: "25/04/2022"
output:
  html_document: 
    toc: yes
    toc_float: yes
    toc_depth: 5
    highlight: kate
    theme: paper
    self_contained: yes
    mode: selfcontained
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Summary of the stats and interpretation


# Libraries 
```{r, warning=FALSE, message=FALSE}
source("./MacroEcol_1_Libraries.R")
library(coda)
```

# Meaning of the PCs

Lower PC1 = higher humidity (vapour, rain and clouds) lower aridity.  

<br>

Lower PC2 = higher solar radiation, higher max temp, more days above 35 and more aridity

<br>
<br>

# PGLS 


# PGLS in multiple Trees

## TOT

```{r}
mudfTOT <- read.csv("../Data/FromCode/MuTPglsResultsTOT.csv")[-1]

rrTOT<- HPDinterval(as.mcmc(mudfTOT))

```

## VIS


```{r}
mudfVIS <- read.csv("../Data/FromCode/MuTPglsResultsVIS.csv")[-1]

rrVIS <- HPDinterval(as.mcmc(mudfVIS))
```


## NIR


```{r}
mudfNIR <- read.csv("../Data/FromCode/MuTPglsResultsNIR.csv")[-1]

rrNIR <- HPDinterval(as.mcmc(mudfNIR))

```

## Res

```{r}

mudfRes <- read.csv("../Data/FromCode/MuTPglsResultsRes.csv")[-1]

rrRes <- HPDinterval(as.mcmc(mudfRes))

```

full summary:


```{r}


Predictor <- c("PC1","PC1 p-val" , 
               "PC2", "PC2 p-val", 
               "Size", "Size p-val", 
               "PC1:size", "PC1:size p-val", 
               "PC2:size", "PC2:size p-val")

rvTOTl <- round(as.numeric(c(rrTOT[1,1],rrTOT[3,1],rrTOT[4,1],rrTOT[6,1],
              rrTOT[7,1],rrTOT[9,1],rrTOT[10,1],rrTOT[12,1],
              rrTOT[13,1],rrTOT[15,1])),3)

rvTOTu <- format(round(as.numeric(c(rrTOT[1,2],rrTOT[3,2],rrTOT[4,2],rrTOT[6,2],
              rrTOT[7,2],rrTOT[9,2],rrTOT[10,2],rrTOT[12,2],
              rrTOT[13,2],rrTOT[15,2])),3),nsmall=3)


rvVISl <- round(as.numeric(c(rrVIS[1,1],rrVIS[3,1],rrVIS[4,1],rrVIS[6,1],
              rrVIS[7,1],rrVIS[9,1],rrVIS[10,1],rrVIS[12,1],
              rrVIS[13,1],rrVIS[15,1])),3)

rvVISu <- format(round(as.numeric(c(rrVIS[1,2],rrVIS[3,2],rrVIS[4,2],rrVIS[6,2],
              rrVIS[7,2],rrVIS[9,2],rrVIS[10,2],rrVIS[12,2],
              rrVIS[13,2],rrVIS[15,2])),3),nsmall=3)



rvNIRl <- round(as.numeric(c(rrNIR[1,1],rrNIR[3,1],rrNIR[4,1],rrNIR[6,1],
              rrNIR[7,1],rrNIR[9,1],rrNIR[10,1],rrNIR[12,1],
              rrNIR[13,1],rrNIR[15,1])),3)

rvNIRu <- format(round(as.numeric(c(rrNIR[1,2],rrNIR[3,2],rrNIR[4,2],rrNIR[6,2],
              rrNIR[7,2],rrNIR[9,2],rrNIR[10,2],rrNIR[12,2],
              rrNIR[13,2],rrNIR[15,2])),3),nsmall=3)

rvResl <- round(as.numeric(c(rrRes[1,1],rrRes[3,1],rrRes[4,1],rrRes[6,1],
              rrRes[7,1],rrRes[9,1],rrRes[10,1],rrRes[12,1],
              rrRes[13,1],rrRes[15,1])),3)

rvResu <- round(as.numeric(c(rrRes[1,2],rrRes[3,2],rrRes[4,2],rrRes[6,2],
              rrRes[7,2],rrRes[9,2],rrRes[10,2],rrRes[12,2],
              rrRes[13,2],rrRes[15,2])),3)


rvTOTi<-paste(rvTOTl,rvTOTu, sep = " ; ")
rvVISi<-paste(rvVISl,rvVISu, sep = " ; ")
rvNIRi<-paste(rvNIRl,rvNIRu, sep = " ; ")
rvResi<-paste(rvResl,rvResu, sep = " ; ")

rvVISi[1] <- cell_spec(rvVISi[1],bold = TRUE, color="#D40481")
rvVISi[2] <- cell_spec(rvVISi[2],bold = TRUE)

rvVISi[5] <- cell_spec(rvVISi[5],bold = TRUE, color="#D40481")
rvVISi[6] <- cell_spec(rvVISi[6],bold = TRUE)

rvVISi[7] <- cell_spec(rvVISi[7],bold = TRUE, color="#D40481")
rvVISi[8] <- cell_spec(rvVISi[8],bold = TRUE)


rvResi[3] <- cell_spec(rvResi[3],bold = TRUE, color="#D40481")
rvResi[4] <- cell_spec(rvResi[4],bold = TRUE)

rvResi[9] <- cell_spec(rvResi[9],bold = TRUE, color="#D40481")
rvResi[10] <- cell_spec(rvResi[10],bold = TRUE)

Resultspgls <- data.frame(Predictor,  
                          "TOT" = rvTOTi,
                          "VIS" = rvVISi,
                          "NIR" = rvNIRi,
                          "Res" = rvResi) 


Resultspgls %>% 
  kbl(align ="c", escape = FALSE) %>%
  kable_classic() %>% 
  add_indent(c(1, 3, 5, 7, 9)) 


```

Summary:

The significant correlations involve visible reflectivity. 


Size **Negative correlation**  
Size:PC1 **Positive correlation**  
Size:PC2 **Negatove correlation** 


