---
title: "Supplementary"
# author: "Laura Ospina-Rozo"
# date: "23/04/2022"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Supplementary Materials


## Correlations between ecological variables

```{r}

# All variables Vegetation and Climate for activity period:
EVarR2P %>%
  kbl() %>%
  kable_paper("hover", full_width = F)

EvarCpP %>%
  kbl() %>%
  kable_paper("hover", full_width = F)


# After removing correlations of R > 0.8
EVarR2 %>%
  kbl() %>%
  kable_paper("hover", full_width = F)

EvarCp %>%
  kbl() %>%
  kable_paper("hover", full_width = F)
```





## The NIR mystery (Old calculations)

Our hypothesis was that more exposed arid environments would correlate to higher NIR/vis Ratio, since higher NIR could be used for thermoregulation. However, we found the opposite pattern: No correlation between NIR and PC2, and lower NIR/Vis ratio in more arid environments: 

```{r eval=FALSE}

ggplot(Cons, aes(x = PC2, y = Ratio)) +
  geom_point(
    size = 3, alpha = 0.4, pch = 21,
    col = "black",
    fill = "#762A83"
  ) +
  geom_smooth(method = "lm") +
  theme_bw() +
  ylim(0, 23) +
  scale_color_brewer(palette = "Accent") +
  theme(legend.position = "none")
```


My explanation: In these beetles higher values of NIR/VIS ratio are found more often in individuals with moderate NIR and very low vis, rather than in beetles with high NIR and moderate vis.\
Thus, higher ratio is inversely correlated with the total reflectivity, and not useful in arid environments with high radiation.

A plot to illustrate this:

```{r eval=FALSE}

ggplot(Cons, aes(full, Ratio)) +
  geom_point(
    size = 3, alpha = 0.3, pch = 21,
    col = "black",
    fill = "#762A83"
  ) +
  xlim(10, 56) +
  ylim(0, 22) +
  theme_bw()
```

So maybe, they all have high NIR reflectance and the ones in more extreme environments would need also to have high VIS reflectance.

-   Compare with other groups of beetles or insects here.

Do they *all* have very high NIR reflecttivity?

```{r eval=FALSE}

p <- ggplot(Cons, aes(NIR, vis)) +
  geom_point(size = 3, alpha = 0.3, col = "#762A83") +
  xlim(0, 100) +
  ylim(0, 70) +
  theme_bw()
ggExtra::ggMarginal(p, type = "histogram", fill = "gray")
```

Not really, there is a lot of variability, but it is important to highlight that the average reflectivity for NIR is r mean(Cons$NIR) %. As shown in the following plot, the highest values of reflectivity in this group are in the NIR spectral band, therefore it is likely to contribute significantly to the results in the total reflectivity (including all wavelengths). 

```{r eval=FALSE}

Diagnostics <-
  Cons %>%
  dplyr::select(full, NIR, vis) %>%
  dplyr::rename(
    All = full,
    VIS = vis
  ) %>%
  dplyr::gather(
    key = spectralband,
    value = Reflectivity
  ) # prepare for ggplot

source("https://raw.githubusercontent.com/datavizpyr/data/master/half_flat_violinplot.R")


ggplot(Diagnostics, aes(spectralband, Reflectivity)) +
  theme_bw() +
  geom_flat_violin(fill = "#762A83", alpha = 0.3) +
  geom_boxplot(width = 0.05, fill = "grey")
```



## Intraspecific Variability


```{r eval=FALSE}

Bla <- read.csv("../Data/20220111ConsolidatedFile.csv")

Tablebla <- table(Bla$spp)

barplot(Tablebla, horiz = TRUE, las = 2, cex.axis = 1, cex.names = 0.9)

length(Tablebla)
names(Bla)
Bla$spp
cases <-
  Bla %>%
  filter(spp == "poro" | spp == "prsi" |
    spp == "hirs" | spp == "smgd" |
    spp == "clor")

ggplot(cases, aes(x = PC1, y = PC2, colour = spp)) +
  geom_point(size = 4, alpha = 0.7) +
  geom_point(size = 4, pch = 21, colour = "black", alpha = 0.7) +
  theme_bw() +
  theme(legend.position = "none") +
  geom_text(alpha = .3, size = 4, aes(label = spp), col = "black")

ggplot(cases, aes(x = spp, y = R_ALL)) +
  geom_boxplot(width = 0.5, fill = "blue", alpha = 0.5) +
  theme_bw() +
  geom_point(size = 3, alpha = 0.4)

ggplot(Bla, aes(x = spp, y = R_ALL)) +
  geom_boxplot(width = 0.5, fill = "blue", alpha = 0.5) +
  theme_bw() +
  geom_point(size = 2, alpha = 0.4) +
  coord_flip()

ggplot(Bla, aes(x = spp, y = R_NIR)) +
  geom_boxplot(width = 0.5, fill = "blue", alpha = 0.5) +
  theme_bw() +
  geom_point(size = 2, alpha = 0.4) +
  coord_flip()


ggplot(Bla, aes(x = spp, y = R_ALL)) +
  geom_boxplot(width = 0.5, fill = "blue", alpha = 0.5) +
  theme_bw() +
  geom_point(size = 2, alpha = 0.4) +
  coord_flip()
```


## Reflectance in a Map

```{r eval=FALSE, echo = FALSE, warning = FALSE, message = FALSE}
library(ozmaps)
library(sf)
oz_states <- ozmaps::ozmap_states # load Australian maps
st_crs(oz_states) <- 4326 # transform have to make due to package problem

ggplot(oz_states) +
  geom_sf() +
  coord_sf(x = c(105.5507, 167.9969), y = c(-43.63203, -9.229287)) +
  geom_point(
    data = refl.plot.dat, # here the coords data has to be the original format, not spatial format
    aes(
      x = lon, y = lat, color = total.refl, # Change here for TOT, NIR or VIS
      size = total.refl
    ), # if want to change size as well, size = PC2
    alpha = 0.5
  ) +
  scale_colour_viridis_c() +
  ggtitle("Total Reflectance") +
  theme_bw()
```
