---
title: "Reflectivity PGLS"
# author: "Laura Ospina-Rozo"
# date: "25/04/2022"
---

# Libraries

```{r, warning=FALSE, message=FALSE}
source("./MacroEcol_1_Libraries.R")
trees_subset_min<-1000
trees_subset_max<-2000
```


# Data Sets

Reflectivity by Individual

```{r}
Cons1 <- read.csv("../Data/FromCode/ConsReflEcolInd.csv")[-1]

Cons1agg <- read.csv("../Data/FromCode/ConsolidatedReflectivitySpp.csv")[-1]


```


Phylogeny (multiple trees)

```{r}
trees <- ape::read.tree("../Data/XMAS_mat2b_bst2ef_set23nn2_pinct.nwk")

MCCtree <- 
  ape::read.nexus("../Data/xmas_mat2b_bst2ef_set23nn2_pinct_med.tre")
```


## Aggregate

In this analysis we will consider interspecific instead of intraspecific variability.

```{r}

# Modify to make it compatible with tree tips
Cons1agg <- as.data.frame(Cons1agg) # convert to a data frame
rownames(Cons1agg) <- Cons1agg[, 1] # make species the row names 
#ConsAgg <- Cons1agg [,2:length(Cons1agg)] # eliminate spp name (redundant)

```

## Match

Make sure that the phylogeny names are consistent in the data frame and the phylogenetic trees

Read and prune the MCC tree

The MCC (Maximum clade credibility) tree used here is the BEAST MCC tree. We did not need to prun the tree. The equivalence between specie sin the tree and data frame was tested in previous steps (tab optical properties). 

The names between data and tree tips match: 

```{r}
# Test if the species are the same
identical(
  length(name.check(MCCtree, Cons1agg$phylogeny_name)$tree_not_data),
  length(Cons1agg$phylogeny_name)
)

```

## Subset

Create subsets for each waveband

```{r}

ALLDataSet <- 
  Cons1agg %>% 
  dplyr::select (-VIS, -NIR, - Res, -FRS) %>% 
  dplyr::rename ("Reflectance" = TOT) 

NIRDataSet <- 
  Cons1agg %>% 
  dplyr::select (-TOT, -VIS, - Res, -FRS) %>% 
  dplyr::rename ("Reflectance" = NIR) 

VISDataSet <- 
  Cons1agg %>% 
  dplyr::select (-TOT, -NIR, - Res, -FRS) %>% 
  dplyr::rename ("Reflectance" = VIS) 

ResDataSet <- 
  Cons1agg %>% 
  dplyr::select (-TOT, -NIR, -VIS, -FRS) %>% 
  dplyr::rename ("Reflectance" = Res)

NmoDataSet <-
  Cons1agg %>% 
  dplyr::select (-TOT, - Res, -FRS) %>% 
  dplyr::rename ("Reflectance" = NIR) 

FRSDataSet <-
 Cons1agg %>% 
  dplyr::select (-TOT, -NIR, -VIS, -Res) %>% 
  dplyr::rename ("Reflectance" = FRS)

```


# Setting up models

note that the function has to be adapted to the data frame and model on each case

## Model 1

PGLS in the MCC

```{r}

comp_data <- comparative.data(
  phy = MCCtree, data = Cons1agg,
  names.col = "phylogeny_name", vcv = TRUE,
  na.omit = FALSE, warn.dropped = TRUE
)

```

## Model 2

PGLS Multiple Trees with 5 predictors + intercept

Source function

note that this function has to be adapted to the data frame and model on each case

```{r warning=FALSE, message=FALSE}
source("8_multiple_pgls_function_C.R")# function C is for reflectance as response
```

Define model


```{r }
MuPGLSMod2 <- Reflectance ~ PC1 + PC2 + size + PC1*size + PC2*size
```



## Model 3

PGLS in multiple trees for NIR contains 6 predictors + intercept. The extra predictor here is the "VIS" reflectance to account for the correlation of these two variables.


```{r warning=FALSE, message=FALSE}
source("9_multiple_pgls_function_D.R")# function D is NIR explained by PCs and VIS
```


Define model

```{r}

MuPGLSMod3 <- Reflectance ~ PC1 + PC2 + size + PC1*size + PC2*size + VIS

```


## Model 4

PGLS Multiple Trees with 3 predictors + intercept

We run simplified models with only one pc for each spectral band including only the predictors that were signifficant in the full model. 
(because the visible reflectance seems to be more correlated to PC1 and the NIR to PC2) 

Source function

note that this function has to be adapted to the data frame and model on each case

```{r warning=FALSE, message=FALSE}
source("10_multiple_pgls_function_E.R")# function C is for reflectance as response
```

Define model

```{r }
MuPGLSMod4 <- Reflectance ~ PC + size + PC*size 
```


## Model 5

PGLS Multiple Trees with 4 predictors + intercept

We run simplified models with only one pc for each spectral band including only the predictors that were signifficant in the full model (because the visible reflectance seems to be more correlated to PC1 and the NIR to PC2). However, for NIR we need to include VIS reflectance as a predictor

Source function

note that this function has to be adapted to the data frame and model on each case

```{r warning=FALSE, message=FALSE}
source("11_multiple_pgls_function_F.R")# function C is for reflectance as response
```

Define model

```{r }
MuPGLSMod5 <- Reflectance ~ PC + size + PC*size + VIS
```




# Results per spectral band

The PGLS model tests if the correlations we found in the previous step remain after correcting by phylogeny. This model does not consider instraspecific variation. We averaged both location and reflectivity and obtained only one value per species. 


## TOT

### MCC Tree

```{r message= FALSE, warnings=FALSE}
pglsmodTOT <- pgls(TOT ~ PC1 + PC2 + size + PC1*size + PC2*size,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

FinMccTotc <- as.numeric(round(summary(pglsmodTOT)$coefficients[,1],3))
FinMccTotp <- as.numeric(round(summary(pglsmodTOT)$coefficients[,4],3)) 

```

None of the variables has an effect in the total reflectance

Test phylogenetic signal using Pagel's lambda:

```{r}

pagelTOTRefl <- Cons1agg$TOT # Define which trait you want to test
names(pagelTOTRefl) <- rownames(Cons1agg) # Row names = tree tips
phylosig(MCCtree, pagelTOTRefl, method = "lambda", test = TRUE, nsim = 999)
# nsim = 999 means testing with 999 randomizations

```

Phylogenetic signal is high. 


### multiple trees


```{r message=FALSE, warning=FALSE}

runsTOT<-lapply(trees[trees_subset_min:trees_subset_max],
                pgls_runC,
                model=MuPGLSMod2,
                dataset=ALLDataSet) 

dfTOT <- ldply (runsTOT, data.frame)

write.csv(dfTOT,"../Data/FromCode/MuTPglsResultsTOT.csv")

FinTotM <- HPDinterval(as.mcmc(dfTOT))

```



## VIS 

### full model

#### MCC Tree

```{r message= FALSE, warnings=FALSE}
pglsmodVIS <- pgls(VIS ~ PC1 + PC2 + size + PC1*size + PC2*size,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

FinMccVisc <- as.numeric(round(summary(pglsmodVIS)$coefficients[,1],3)) 
FinMccVisp <- as.numeric(round(summary(pglsmodVIS)$coefficients[,4],3))

```

Test phylogenetic signal using Pagel's lambda:

```{r}

pagelVISRefl <- Cons1agg$VIS # Define which trait you want to test
names(pagelVISRefl) <- rownames(Cons1agg) # Row names = tree tips
phylosig(MCCtree, pagelVISRefl, method = "lambda", test = TRUE, nsim = 999)
# nsim = 999 means testing with 999 randomizations

```

Phylogenetic signal is high. 


#### multiple trees


```{r message=FALSE, warning=FALSE}

runsVIS<-lapply(trees[trees_subset_min:trees_subset_max],
                pgls_runC,
                model=MuPGLSMod2,
                dataset=VISDataSet) 

dfVIS <- ldply (runsVIS, data.frame)

write.csv(dfVIS,"../Data/FromCode/MuTPglsResultsVIS.csv")

FinVisM <- HPDinterval(as.mcmc(dfVIS))

```


### simple model


#### MCC Tree

```{r message= FALSE, warnings=FALSE}
spglsmodVIS <- pgls(VIS ~ PC1 + size + PC1*size,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

summary(spglsmodVIS) 

sFinMccVisc <- as.numeric(round(summary(spglsmodVIS)$coefficients[,1],3)) 
sFinMccVisp <- as.numeric(round(summary(spglsmodVIS)$coefficients[,4],3))

```

#### multiple trees

First step is to modify the data frame. 

```{r}
SimpleVIS <- 
  VISDataSet %>% 
  dplyr::select(phylogeny_name, Reflectance, size, PC1) %>% 
  dplyr::rename(PC = PC1)

SimpleVIS <- as.data.frame(SimpleVIS)

```

Now run the model

```{r message=FALSE, warning=FALSE}

runsVISsimple<-lapply(trees[trees_subset_min:trees_subset_max],
                      pgls_runE,
                      model=MuPGLSMod4,
                      dataset=SimpleVIS) 

dfVISsimple <- ldply (runsVISsimple, data.frame)

FinVisS <- HPDinterval(as.mcmc(dfVISsimple))

```


## NIR 

### Full model

#### MCC Tree

```{r message= FALSE, warnings=FALSE}
pglsmodNIR <- pgls(NIR ~ PC1 + PC2 + size + PC1*size + PC2*size + VIS,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

FinMccNirc <- as.numeric(round(summary(pglsmodNIR)$coefficients[,1],3)) 
FinMccNirp <- as.numeric(round(summary(pglsmodNIR)$coefficients[,4],3))

```

Results after correcting by phylogeny: 

None of the variables has an effect in the NIR reflectance

Test phylogenetic signal using Pagel's lambda:

```{r}

pagelNIRRefl <- Cons1agg$NIR # Define which trait you want to test
names(pagelNIRRefl) <- rownames(Cons1agg) # Row names = tree tips
phylosig(MCCtree, pagelNIRRefl, method = "lambda", test = TRUE, nsim = 999)
# nsim = 999 means testing with 999 randomizations

```

Phylogenetic signal is high. 


#### multiple trees 



```{r message=FALSE, warning=FALSE}

runsNIR<-lapply(trees[trees_subset_min:trees_subset_max],
                pgls_runD,
                model=MuPGLSMod3,
                dataset=NmoDataSet) 

dfNIR <- ldply (runsNIR, data.frame)

write.csv(dfNIR,"../Data/FromCode/MuTPglsResultsNmo.csv")

FinNirM <- HPDinterval(as.mcmc(dfNIR))

```





### Simple model

#### MCC Tree

```{r message= FALSE, warnings=FALSE}
spglsmodNIR <- pgls(NIR ~ PC2 + size + PC2*size + VIS,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

sFinMccNirc <- as.numeric(round(summary(spglsmodNIR)$coefficients[,1],3)) 
sFinMccNirp <- as.numeric(round(summary(spglsmodNIR)$coefficients[,4],3))

```


#### multiple trees


First step is to modify the data frame. 

```{r}

SimpleNIR <- 
  NmoDataSet %>% 
  dplyr::select(phylogeny_name, Reflectance, size, VIS, PC2) %>% 
  dplyr::rename(PC = PC2)

SimpleNIR <- as.data.frame(SimpleNIR)
head(SimpleNIR)
```

Now run the model

```{r message=FALSE, warning=FALSE}

runsNIRsimple<-lapply(trees[trees_subset_min:trees_subset_max],
                      pgls_runF,
                      model=MuPGLSMod5,
                      dataset=SimpleNIR) 

dfNIRsimple <- ldply (runsNIRsimple, data.frame)

FinNirS <- HPDinterval(as.mcmc(dfNIRsimple))

```



## Res

(i.e. residuals between NIR ~ VIS)

### Full model

#### MCC Tree


```{r message= FALSE}
pglsmodRes <- pgls(Res ~ PC1 + PC2 + size + PC1*size + PC2*size,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

FinMccResc <- as.numeric(round(summary(pglsmodRes)$coefficients[,1],3)) 
FinMccResp <- as.numeric(round(summary(pglsmodRes)$coefficients[,4],3))

```


Test phylogenetic signal using Pagel's lambda:

```{r}

pagelRes <- Cons1agg$Res # Define which trait you want to test
names(pagelRes) <- rownames(Cons1agg) # Row names = tree tips
phylosig(MCCtree, pagelRes, method = "lambda", test = TRUE, nsim = 999)
# nsim = 999 means testing with 999 randomizations

```

Phylogenetic signal is very high

#### multiple trees

(i.e. residuals between NIR ~ VIS)

```{r message=FALSE, warning=FALSE}

runsRes<-lapply(trees[trees_subset_min:trees_subset_max],
                pgls_runC,
                model=MuPGLSMod2,
                dataset=ResDataSet) 

dfRes <- ldply (runsRes, data.frame)

write.csv(dfRes,"../Data/FromCode/MuTPglsResultsRes.csv")

FinResM <- HPDinterval(as.mcmc(dfRes))

```



### Simple model

#### MCC Tree

```{r message= FALSE}
spglsmodRes <- pgls(Res ~ PC2 + size + PC2*size,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

sFinMccResc <- as.numeric(round(summary(spglsmodRes)$coefficients[,1],3)) 
sFinMccResp <- as.numeric(round(summary(spglsmodRes)$coefficients[,4],3))

```

#### multiple trees

First step is to modify the data frame. 

```{r}
SimpleRes <- 
  ResDataSet %>% 
  dplyr::select(phylogeny_name, Reflectance, size, PC2) %>% 
  dplyr::rename(PC = PC2)

SimpleRes <- as.data.frame(SimpleRes)

```

Now run the model

```{r message=FALSE, warning=FALSE}

runsRessimple<-lapply(trees[trees_subset_min:trees_subset_max],
                      pgls_runE,
                      model=MuPGLSMod4,
                      dataset=SimpleRes) 

dfRessimple <- ldply (runsRessimple, data.frame)

FinResS <-HPDinterval(as.mcmc(dfRessimple))


```


## FRS


(i.e. residuals between NIR ~ VIS corrected by phylogeny)

### Full model

#### MCC Tree


```{r message= FALSE}
pglsmodFRS <- pgls(FRS ~ PC1 + PC2 + size + PC1*size + PC2*size,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

FinMccFRSc <- as.numeric(round(summary(pglsmodFRS)$coefficients[,1],3)) 
FinMccFRSp <- as.numeric(round(summary(pglsmodFRS)$coefficients[,4],3))

```


Test phylogenetic signal using Pagel's lambda:

```{r}

pagelFRS <- Cons1agg$FRS # Define which trait you want to test
names(pagelFRS) <- rownames(Cons1agg) # Row names = tree tips
phylosig(MCCtree, pagelFRS, method = "lambda", test = TRUE, nsim = 999)
# nsim = 999 means testing with 999 randomizations

```

Phylogenetic signal is very high

#### multiple trees

(i.e. Residuals between NIR ~ VIS corrected by phylogeny)

```{r message=FALSE, warning=FALSE}

runsFRS<-lapply(trees[trees_subset_min:trees_subset_max],
                pgls_runC,
                model=MuPGLSMod2,
                dataset=FRSDataSet) 

dfFRS <- ldply (runsFRS, data.frame)

write.csv(dfFRS,"../Data/FromCode/MuTPglsFRSultsFRS.csv")

FinFRSM <- HPDinterval(as.mcmc(dfFRS))

```



### Simple model

#### MCC Tree

```{r message= FALSE}
spglsmodFRS <- pgls(FRS ~ PC2 + size + PC2*size,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

sFinMccFRSc <- as.numeric(round(summary(spglsmodFRS)$coefficients[,1],3)) 
sFinMccFRSp <- as.numeric(round(summary(spglsmodFRS)$coefficients[,4],3))

```

#### multiple trees

First step is to modify the data frame. 

```{r}
SimpleFRS <- 
  FRSDataSet %>% 
  dplyr::select(phylogeny_name, Reflectance, size, PC2) %>% 
  dplyr::rename(PC = PC2)

SimpleFRS <- as.data.frame(SimpleFRS)

```

Now run the model

```{r message=FALSE, warning=FALSE}

runsFRSsimple<-lapply(trees[trees_subset_min:trees_subset_max],
                      pgls_runE,
                      model=MuPGLSMod4,
                      dataset=SimpleFRS) 

dfFRSsimple <- ldply (runsFRSsimple, data.frame)

FinFRSS <-HPDinterval(as.mcmc(dfFRSsimple))


```



# Final results

## Full models

### MCC Tree

```{r message=FALSE, warning=FALSE}

Predictor <- c("PC1","PC1 p-val" , 
               "PC2", "PC2 p-val", 
               "Size", "Size p-val",
               "VIS", "VIS p-val",
               "PC1:size", "PC1:size p-val", 
               "PC2:size", "PC2:size p-val")

# Arrange the vectors to build the data frame
# New vectors alternate coefficient and p-values to match "predictors"

Toti <- as.character(as.numeric(c(rbind((c(
            FinMccTotc[2:4],"NA",FinMccTotc[5:6])),
                (c(FinMccTotp[2:4],"NA",FinMccTotp[5:6]))))))

Visi <- as.character(as.numeric(c(rbind((c(
            FinMccVisc[2:4],"NA",FinMccVisc[5:6])),
                (c(FinMccVisp[2:4],"NA",FinMccVisp[5:6]))))))

Niri <- as.character(as.numeric(c(rbind(
            FinMccNirc[2:7], FinMccNirp[2:7]))))

Resi <- as.character(as.numeric(c(rbind((c(
            FinMccResc[2:4],"NA",FinMccResc[5:6])),
                (c(FinMccResp[2:4],"NA",FinMccResp[5:6]))))))
  
# This section colours the signifficant p-values and their coefficients

Visi[1] <- cell_spec(Visi[1],bold = TRUE, color="#D40481")
Visi[2] <- cell_spec(Visi[2],bold = TRUE)

Visi[5] <- cell_spec(Visi[5],bold = TRUE, color="#D40481")
Visi[6] <- cell_spec(Visi[6],bold = TRUE)

Visi[9] <- cell_spec(Visi[9],bold = TRUE, color="#D40481")
Visi[10] <- cell_spec(Visi[10],bold = TRUE)

Niri[3] <- cell_spec(Niri[3],bold = TRUE, color="#D40481")
Niri[4] <- cell_spec(Niri[4],bold = TRUE)

Niri[7] <- cell_spec(Niri[7],bold = TRUE, color="#D40481")
Niri[8] <- cell_spec(Niri[8],bold = TRUE)

Niri[11] <- cell_spec(Niri[11],bold = TRUE, color="#D40481")
Niri[12] <- cell_spec(Niri[12],bold = TRUE)

Resi[3] <- cell_spec(Resi[3],bold = TRUE, color="#D40481")
Resi[4] <- cell_spec(Resi[4],bold = TRUE)

Resi[11] <- cell_spec(Resi[11],bold = TRUE, color="#D40481")
Resi[12] <- cell_spec(Resi[12],bold = TRUE)

# Assemble the table

Resultspgls <- data.frame(Predictor,  
                          "TOT" = Toti,
                          "VIS" = Visi,
                          "NIR" = Niri,
                          "Res" = Resi) 

Resultspgls %>% 
  kbl(align ="c", escape = FALSE) %>%
  kable_classic() %>% 
  add_indent(c(1, 3, 5, 7, 9)) 


```


### multiple trees

```{r}

rvTOTl <- as.character(
            round(as.numeric(c(
              FinTotM[1,1],FinTotM[3,1],FinTotM[4,1],FinTotM[6,1],
              FinTotM[7,1],FinTotM[9,1],"NA","NA",
              FinTotM[10,1],FinTotM[12,1],
              FinTotM[13,1],FinTotM[15,1])),3))

rvTOTu <- as.character(
            format(round(as.numeric(c(
              FinTotM[1,2],FinTotM[3,2],FinTotM[4,2],FinTotM[6,2],
              FinTotM[7,2],FinTotM[9,2],"NA","NA",
              FinTotM[10,2],FinTotM[12,2],
              FinTotM[13,2],FinTotM[15,2])),3),nsmall=3))


rvVISl <- as.character(
          format(round(as.numeric(c(
              FinVisM[1,1],FinVisM[3,1],FinVisM[4,1],FinVisM[6,1],
              FinVisM[7,1],FinVisM[9,1],"NA","NA",
              FinVisM[10,1],FinVisM[12,1],
              FinVisM[13,1],FinVisM[15,1])),3),nsmall=3))

rvVISu <- as.character(
            format(round(as.numeric(c(
              FinVisM[1,2],FinVisM[3,2],FinVisM[4,2],FinVisM[6,2],
              FinVisM[7,2],FinVisM[9,2],"NA","NA",
              FinVisM[10,2],FinVisM[12,2],
              FinVisM[13,2],FinVisM[15,2])),3),nsmall=3))


rvNIRl <- as.character(
            format(round(as.numeric(c(
              FinNirM[1,1],FinNirM[3,1],FinNirM[4,1],FinNirM[6,1],
              FinNirM[7,1],FinNirM[9,1],FinNirM[10,1],FinNirM[12,1],
              FinNirM[13,1],FinNirM[15,1], FinNirM[16,1],FinNirM[18,1]
              )),3),nsmall=3))

rvNIRu <- as.character(
           format(round(as.numeric(c(
              FinNirM[1,2],FinNirM[3,2],FinNirM[4,2],FinNirM[6,2],
              FinNirM[7,2],FinNirM[9,2],FinNirM[10,2],FinNirM[12,2],
              FinNirM[13,2],FinNirM[15,2], FinNirM[16,2],FinNirM[18,2]
              )),3),nsmall=3))

rvResl <- as.character(
            format(round(as.numeric(c(
              FinResM[1,1],FinResM[3,1],FinResM[4,1],FinResM[6,1],
              FinResM[7,1],FinResM[9,1],"NA","NA",
              FinResM[10,1],FinResM[12,1],
              FinResM[13,1],FinResM[15,1])),3),nsmall=3))

rvResu <- as.character(
            format(round(as.numeric(c(
              FinResM[1,2],FinResM[3,2],FinResM[4,2],FinResM[6,2],
              FinResM[7,2],FinResM[9,2],"NA","NA",
              FinResM[10,2],FinResM[12,2],
              FinResM[13,2],FinResM[15,2])),3),nsmall=3))


rvTOTi<-paste(rvTOTl,rvTOTu, sep = " ; ")
rvVISi<-paste(rvVISl,rvVISu, sep = " ; ")
rvNIRi<-paste(rvNIRl,rvNIRu, sep = " ; ")
rvResi<-paste(rvResl,rvResu, sep = " ; ")

rvVISi[1] <- cell_spec(rvVISi[1],bold = TRUE, color="#367D91")
rvVISi[2] <- cell_spec(rvVISi[2],bold = TRUE, color="#B2B9BF")

rvVISi[5] <- cell_spec(rvVISi[5],bold = TRUE, color="#D40481")
rvVISi[6] <- cell_spec(rvVISi[6],bold = TRUE)

rvVISi[9] <- cell_spec(rvVISi[9],bold = TRUE, color="#367D91")
rvVISi[10] <- cell_spec(rvVISi[10],bold = TRUE,  color="#B2B9BF")

rvNIRi[3] <- cell_spec(rvNIRi[3],bold = TRUE, color="#D40481")
rvNIRi[4] <- cell_spec(rvNIRi[4],bold = TRUE)

rvNIRi[7] <- cell_spec(rvNIRi[7],bold = TRUE, color="#D40481")
rvNIRi[8] <- cell_spec(rvNIRi[8],bold = TRUE)

rvNIRi[11] <- cell_spec(rvNIRi[11],bold = TRUE, color="#D40481")
rvNIRi[12] <- cell_spec(rvNIRi[12],bold = TRUE)

rvResi[3] <- cell_spec(rvResi[3],bold = TRUE, color="#D40481")
rvResi[4] <- cell_spec(rvResi[4],bold = TRUE)

rvResi[11] <- cell_spec(rvResi[11],bold = TRUE, color="#D40481")
rvResi[12] <- cell_spec(rvResi[12],bold = TRUE)

Resultspgls <- data.frame(Predictor,  
                          "TOT" = rvTOTi,
                          "VIS" = rvVISi,
                          "NIR" = rvNIRi,
                          "Res" = rvResi) 


Resultspgls %>% 
  kbl(align ="c", escape = FALSE) %>%
  kable_classic() %>% 
  add_indent(c(1, 3, 5, 7, 9)) 


```


## Simple models

### MCC Tree

We run reduced models with the predictors that were signifficant in the MCC tree to confirm the patterns and to reduce issues with the abnormal termination in some trees (because in larger models some parameters can’t be calculated when using particular trees)

In this table PC represents the relevant PC for each band: For VIS it is PC1 and for NIR/Res it is PC2. This is also true for the correspondent interactions.

```{r message=FALSE, warning=FALSE}

sPredictor <- c("PC","PC p-val" , 
               "Size", "Size p-val",
               "VIS", "VIS p-val", 
               "PC:size", "PC:size p-val")

# Arrange the vectors to build the data frame
# New vectors alternate coefficient and p-values to match "predictors"

sVisi <- as.character(as.numeric(c(rbind((c(
            sFinMccVisc[2:3],"NA",sFinMccVisc[4])),
                (c(sFinMccVisp[2:3],"NA",sFinMccVisp[4]))))))

sNiri <- as.character(as.numeric(c(rbind(
            sFinMccNirc[2:5], sFinMccNirp[2:5]))))

sResi <- as.character(as.numeric(c(rbind((c(
            sFinMccResc[2:3],"NA",sFinMccResc[4])),
                (c(sFinMccResp[2:3],"NA",sFinMccResp[4]))))))
  
# This section colours the signifficant p-values and their coefficients

sVisi[1] <- cell_spec(sVisi[1],bold = TRUE, color="#D40481")
sVisi[2] <- cell_spec(sVisi[2],bold = TRUE)

sVisi[3] <- cell_spec(sVisi[3],bold = TRUE, color="#D40481")
sVisi[4] <- cell_spec(sVisi[4],bold = TRUE)

sVisi[7] <- cell_spec(sVisi[7],bold = TRUE, color="#D40481")
sVisi[8] <- cell_spec(sVisi[8],bold = TRUE)


sNiri[1] <- cell_spec(sNiri[1],bold = TRUE, color="#D40481")
sNiri[2] <- cell_spec(sNiri[2],bold = TRUE)

sNiri[5] <- cell_spec(sNiri[5],bold = TRUE, color="#D40481")
sNiri[6] <- cell_spec(sNiri[6],bold = TRUE)

sNiri[7] <- cell_spec(sNiri[7],bold = TRUE, color="#D40481")
sNiri[8] <- cell_spec(sNiri[8],bold = TRUE)


sResi[1] <- cell_spec(sResi[1],bold = TRUE, color="#D40481")
sResi[2] <- cell_spec(sResi[2],bold = TRUE)

sResi[7] <- cell_spec(sResi[7],bold = TRUE, color="#D40481")
sResi[8] <- cell_spec(sResi[8],bold = TRUE)

# Assemble the table

sResultspgls <- data.frame(sPredictor,  
                          "VIS" = sVisi,
                          "NIR" = sNiri,
                          "Res" = sResi) 

sResultspgls %>% 
  kbl(align ="c", escape = FALSE) %>%
  kable_classic() %>% 
  add_indent(c(1, 3, 5, 7)) 


```

### multiple trees


```{r}

srvVISl <- as.character(
  format(round(as.numeric(c(
              FinVisS[1,1],FinVisS[3,1],
              FinResS[4,1],FinVisS[6,1],"NA","NA",
              FinVisS[7,1],FinVisS[9,1])),3),nsmall=3))

srvVISu <- as.character(
            format(round(as.numeric(c(
              FinVisS[1,2],FinVisS[3,2],
              FinVisS[4,2],FinVisS[6,2],"NA","NA",
              FinVisS[7,2],FinVisS[9,2])),3),nsmall=3))


srvNIRl <- as.character(
            format(round(as.numeric(c(
              FinNirS[1,1],FinNirS[3,1],
              FinNirS[4,1],FinNirS[6,1],
              FinNirS[7,1],FinNirS[9,1],
              FinNirS[10,1],FinNirS[12,1]
              )),3),nsmall=3))

srvNIRu <- as.character(
           format(round(as.numeric(c(
              FinNirS[1,2],FinNirS[3,2],
              FinNirS[4,2],FinNirS[6,2],
              FinNirS[7,2],FinNirS[9,2],
              FinNirS[10,2],FinNirS[12,2]
              )),3),nsmall=3))

srvResl <- as.character(
            format(round(as.numeric(c(
              FinResS[1,1],FinResS[3,1],
              FinResS[4,1],FinResS[6,1],"NA","NA",
              FinResS[7,1],FinResS[9,1])),3),nsmall=3))

srvResu <- as.character(
            format(round(as.numeric(c(
              FinResS[1,2],FinResS[3,2],
              FinResS[4,2],FinResS[6,2],"NA","NA",
              FinResS[7,2],FinResS[9,2])),3),nsmall=3))


srvVISi<-paste(srvVISl,srvVISu, sep = " ; ")
srvNIRi<-paste(srvNIRl,srvNIRu, sep = " ; ")
srvResi<-paste(srvResl,srvResu, sep = " ; ")

srvVISi[1] <- cell_spec(srvVISi[1],bold = TRUE, color="#D40481")
srvVISi[2] <- cell_spec(srvVISi[2],bold = TRUE)

srvVISi[3] <- cell_spec(srvVISi[3],bold = TRUE, color="#D40481")
srvVISi[4] <- cell_spec(srvVISi[4],bold = TRUE)

srvVISi[7] <- cell_spec(srvVISi[7],bold = TRUE, color="#D40481")
srvVISi[8] <- cell_spec(srvVISi[8],bold = TRUE)

srvNIRi[1] <- cell_spec(srvNIRi[1],bold = TRUE, color="#D40481")
srvNIRi[2] <- cell_spec(srvNIRi[2],bold = TRUE)

srvNIRi[5] <- cell_spec(srvNIRi[5],bold = TRUE, color="#D40481")
srvNIRi[6] <- cell_spec(srvNIRi[6],bold = TRUE)

srvNIRi[7] <- cell_spec(srvNIRi[7],bold = TRUE, color="#D40481")
srvNIRi[8] <- cell_spec(srvNIRi[8],bold = TRUE)

srvResi[1] <- cell_spec(srvResi[1],bold = TRUE, color="#D40481")
srvResi[2] <- cell_spec(srvResi[2],bold = TRUE)

srvResi[7] <- cell_spec(srvResi[7],bold = TRUE, color="#D40481")
srvResi[8] <- cell_spec(srvResi[8],bold = TRUE)

smResultspgls <- data.frame(sPredictor,
                          "VIS" = srvVISi,
                          "NIR" = srvNIRi,
                          "Res" = srvResi) 


smResultspgls %>% 
  kbl(align ="c", escape = FALSE) %>%
  kable_classic() %>% 
  add_indent(c(1, 3, 5, 7)) 


```

<br>
<br>

# PGLS Assumptions 

Residuals should be normally distributed and should not have any extra patterns after fitting the model

```{r}
par(mfrow=c(2,2))
plot(pglsmodTOT)
plot(pglsmodVIS)
plot(pglsmodNIR)
plot(pglsmodRes)
plot(pglsmodFRS)
```

<br>
<br>

# Interactions

To understand the interaction terms we explored the relationships between the PC value and the reflectance dividing the beetle species into small and large.  

Firstly, prepare data frames

```{r}

VISSmall<-
  SimpleVIS %>% # visible reflectance
  dplyr::filter(size<2.2) # Small beetles

VISLarge<-
  SimpleVIS %>% # visible reflectance
  dplyr::filter(size>2.2) # large beetles

ProbPol <-
  SimpleVIS %>%
  dplyr::filter( #if we want to consider only polarized beetles
    phylogeny_name != "Paraschizognathus_ocularis" &
    phylogeny_name != "Paraschizognathus_prasinus" &
    phylogeny_name != "Paraschizognathus_olivaceous" &
    phylogeny_name != "Anoplognathus_prasinus" &
    phylogeny_name != "Xylonichus_sp") # these all have white underlay


VISSmallp<-
  ProbPol %>% 
  dplyr::filter(size<2.2) # small beetles

VISLargep<-
  ProbPol %>% 
  dplyr::filter(size>2.2) # large beetles


ResSmall<-
  SimpleRes %>% # residuals between the relationship NIR~VIS
  dplyr::filter(size<2.5) # small beetles

ResLarge<-
  SimpleRes %>% 
  dplyr::filter(size>2.5) # Large beetles
  
```


Subsets for plots

```{r}

ToPlotInt <-
  Cons1 %>%
  dplyr::select(-phylogeny_name) %>%
  mutate("spp" = substr(ind, 1, 4)) %>%
  select(-1) %>%
  dplyr::group_by(spp) %>%
  dplyr::summarise(
    meanAll = mean(R_ALL),
    meanVIS = mean(R_VIS),
    meanNIR = mean(R_NIR),
    meanRes = mean(Res),
    meanPC1 = mean(PC1),
    meanPC2 = mean(PC2),
    meanSize = mean(size),
    sdAll = sd(R_ALL),
    sdVIS = sd(R_VIS),
    sdNIR = sd(R_NIR),
    sdRes = sd(Res),
    sdPC1 = sd(PC1),
    sdPC2 = sd(PC2),
    sdSize = sd(size)
  )

names(ToPlotInt)

plotVisSmall <- 
  ToPlotInt %>% 
  dplyr::filter(meanSize<2.2) %>%  # Small beetles
  dplyr::select(1,3,6,8,10,13,15)

plotVisLarge <- 
  ToPlotInt %>% 
  dplyr::filter(meanSize>2.2) %>%  # Large beetles 
  dplyr::select(1,3,6,8,10,13,15)

plotNirSmall <-
  ToPlotInt %>% 
  dplyr::filter(meanSize<2.5) %>%  # Small beetles
  dplyr::select(1,5,7,8,12,14,15)

plotNirLarge <-
  ToPlotInt %>% 
  dplyr::filter(meanSize>2.5) %>%  # Large beetles
  dplyr::select(1,5,7,8,12,14,15)

head(plotNirSmall)
```


## Preliminary 

1) Relationship between vis reflectance and size. 

This relationship is intensified if the most reflective beetles are removed. The species A. aures, A. parvulus and A. roseus.

```{r}

AllBeet <- lm(VISDataSet$Reflectance ~ VISDataSet$size)
summary(AllBeet)

AA <- # removing the most reflective beetles
  VISDataSet %>% 
  dplyr::filter(phylogeny_name != "Anoplognathus_aureus" &
                phylogeny_name != "Anoplognathus_parvulus" &
                phylogeny_name != "Anoplostethus_roseus") 

SubsetBeet <-lm(AA$Reflectance ~ AA$size)
summary(SubsetBeet)


```

If these species are removed, larger beetles reflect more visible light. 

2) PC1

We divided the beetles into two groups large beetles > 2.2 cm and small beetles < 2.2 cm.

** If I remove the non-polarized beetles, the pattern remains the same.

```{r message=FALSE, warning=FALSE}

par(mfrow=c(1,2))
plot(VISSmall$Reflectance ~ VISSmall$PC, 
     xlab="PC1", ylab = "Reflectance",  main="Small beetles (<2.2cm)")
plot(VISLarge$Reflectance ~ VISLarge$PC,
     xlab="PC1", ylab = "Reflectance", main="Large beetles (>2.2cm)")

dumModVs <- lm(VISSmall$Reflectance ~ VISSmall$PC)
summary(dumModVs)

dumModVl <- lm(VISLarge$Reflectance ~ VISLarge$PC) 
summary(dumModVl)

```

Here, there seems to be a negative relationship between the PC1 and the reflectance for small beetles. But the slope does not seem to be significant. 


Plots for NIR light

We separated the beetles into two groups large beetles > 2.5 cm and small beetles < 2.5 cm.

```{r}
par(mfrow=c(1,2))
plot((ResDataSet[ResDataSet$size<2.5,])$PC2,
     (ResDataSet[ResDataSet$size<2.5,])$Reflectance,
     ylab="Reflectance", xlab="PC2", main="Small beetles (<2.5cm)")
plot((ResDataSet[ResDataSet$size>2.5,])$PC2,
     (ResDataSet[ResDataSet$size>2.5,])$Reflectance,
     ylab="Reflectance", xlab="PC2", main="Large beetles (>2.5cm)")
```


```{r}
dumModNb <- lm(ResDataSet$Reflectance ~ ResDataSet$PC2) # All together
summary(dumModNb)

dumModNs <- lm(ResSmall$Reflectance ~ ResSmall$PC) # size < 2.5
summary(dumModNs)

dumModNl <- lm(ResLarge$Reflectance ~ ResLarge$PC) # size > 2.5
summary(dumModNl)
```

There is a positive correlation between PC2 and NIR (residuals NIR~VIS) but this is only valid for small beetles. 
For small beetles, the NIR reflectance is greater in fresh environments. This is opposite to the original hypothesis in which we expected more NIR in more arid and hot environments. 

<br>


## Predictions

We calculated the expected values of visible and NIR reflectance for the two groups of beetles, small and large based on the large full model. 

Fos the visible reflectance we only graphed the PC1 since PC2 did not have a signifficant effect in reflectance. For NIR reflectance we graphed only PC2.

```{r}

# Small beetles VIS

## set values for predictors: 
SVPC1 <- seq(range(plotVisSmall$meanPC1)[1],
             range(plotVisSmall$meanPC1)[2],0.01) # A range of PC1 values

SVPC2 <- rep(mean(VISDataSet$PC2),length(SVPC1)) # The mean PC2 for all beetles 

SVsize <- rep(mean(plotVisSmall$meanSize),
              length(SVPC1)) # mean size of the small beetles

new1<-data.frame("PC1" = SVPC1, "PC2" = SVPC2, "size" = SVsize) # data frame

ref1<-predict(pglsmodVIS, newdata = new1, 
              type = "response") # Expected reflectance

trend1<-data.frame(ref1,SVPC1) # PC1 values and expected reflectance joint
trend1$invSVPC1<- trend1$SVPC1*-1

# Large beetles VIS

LVPC1 <- seq(range(plotVisLarge$meanPC1)[1],
             range(plotVisLarge$meanPC1)[2],0.01) # A range of PC1 values

LVPC2 <- rep(mean(VISDataSet$PC2),length(LVPC1)) # The mean PC2 for all beetles

LVsize <- rep(mean(plotVisLarge$meanSize),
              length(LVPC1)) # mean size of the large beetles

new2<-data.frame("PC1" = LVPC1, "PC2" = LVPC2, "size" = LVsize) # data frame 

ref2<-predict(pglsmodVIS, newdata = new2, 
              type = "response") # Expected reflectance

trend2<-data.frame(ref2,LVPC1) # PC1 values and expected reflectance joint
trend2$invLVPC1 <- trend2$LVPC1*-1


# Small beetles NIR

SNPC2 <- seq(range(plotNirSmall$meanPC2)[1],
             range(plotNirSmall$meanPC2)[2],0.01) # A range of PC2 values

SNPC1 <- rep(mean(ResDataSet$PC1),length(SNPC2)) # The mean PC1 for all beetles

SNsize <- rep((mean(plotNirSmall$meanSize)# mean size of the small beetles
               -0.2), # adjusted for visualization purposes
              length(SNPC2)) 

new3<-data.frame("PC1" = SNPC1, "PC2" = SNPC2, "size" = SNsize) # data frame 

ref3<-predict(pglsmodRes, newdata = new3, 
              type = "response") # Expected reflectance

trend3 <- data.frame(ref3,SNPC2)
trend3$invSNPC2 <- trend3$SNPC2*-1



# Large beetles NIR

LNPC2 <- seq(range(plotNirLarge$meanPC2)[1],
             range(plotNirLarge$meanPC2)[2],0.01) # A range of PC1 values

LNPC1 <- rep(mean(ResDataSet$PC1),length(LNPC2)) # The mean PC2 for all beetles

LNsize <- rep(mean(plotNirLarge$meanSize),
              length(LNPC2)) # mean size of the large beetles

new4<-data.frame("PC1" = LNPC1, "PC2" = LNPC2, "size" = LNsize) # data frame 

ref4<-predict(pglsmodRes, newdata = new4, 
              type = "response") # Expected reflectance

trend4 <- data.frame(ref4,LNPC2)
trend4$invLNPC2 <- trend4$LNPC2*-1

```


## Figures


Plots

PC axis were inverted here so that they are easy to interpret


```{r message=FALSE, warning=FALSE}
PVS <- ggplot(plotVisSmall, aes(x = -meanPC1, y = meanVIS)) +
  geom_errorbar(aes(
    ymin = meanVIS - sdVIS,
    ymax = meanVIS + sdVIS
  ),
  col = "#cecec2"
  ) +
  geom_errorbarh(aes(
    xmin = -meanPC1 - sdPC1,
    xmax = -meanPC1 + sdPC1
  ),
  col = "#cecec2"
  ) +
  geom_point(
    size = 2, pch = 21, fill = "#648fff",
    colour = "black", alpha = 0.9
  ) +
  ylim(0,40)+
  xlim(-2.8,5)+
  theme_minimal() +
  theme(legend.position = "none")+
  geom_line(aes(x= invSVPC1, y= ref1), data=trend1)+
  xlab("Humidity (-PC1)") +
  ylab ("VIS reflectivity (%)")


PVL <- ggplot(plotVisLarge, aes(x = -meanPC1, y = meanVIS)) +
  geom_errorbar(aes(
    ymin = meanVIS - sdVIS,
    ymax = meanVIS + sdVIS
  ),
  col = "#cecec2"
  ) +
  geom_errorbarh(aes(
    xmin = -meanPC1 - sdPC1,
    xmax = -meanPC1 + sdPC1
  ),
  col = "#cecec2"
  ) +
  geom_point(
    size = 2, pch = 21, fill = "#ff7200",
    colour = "black", alpha = 0.9
  ) +
  ylim(0,40)+
  xlim(-2.8,4)+
  theme_minimal() +
  theme(legend.position = "none")+
  geom_line(aes(x= invLVPC1, y= ref2), data=trend2) +
  xlab("Humidity (-PC1)") +
  ylab ("VIS reflectivity (%)")

PNS <- ggplot(plotNirSmall, aes(x = -meanPC2, y = meanRes)) +
  geom_errorbar(aes(
    ymin = meanRes - sdRes,
    ymax = meanRes + sdRes
  ),
  col = "#cecec2"
  ) +
  geom_errorbarh(aes(
    xmin = -meanPC2 - sdPC2,
    xmax = -meanPC2 + sdPC2
  ),
  col = "#cecec2"
  ) +
  geom_point(
    size = 2, pch = 21, fill = "#ff2c85",
    colour = "black", alpha = 0.9
  ) +
  ylim(-20,40)+
  xlim(-4,4)+
  theme_minimal() +
  theme(legend.position = "none")+
  geom_line(aes(x= invSNPC2, y= ref3), data=trend3)  +
  xlab("Aridity & Radiation (-PC2)") +
  ylab ("NIR (res) reflectivity (%)")

PNL <- ggplot(plotNirLarge, aes(x = -meanPC2, y = meanRes)) +
  geom_errorbar(aes(
    ymin = meanRes - sdRes,
    ymax = meanRes + sdRes
  ),
  col = "#cecec2"
  ) +
  geom_errorbarh(aes(
    xmin = -meanPC2 - sdPC2,
    xmax = -meanPC2 + sdPC2
  ),
  col = "#cecec2"
  ) +
  geom_point(
    size = 2, pch = 21, fill = "#ffb000",
    colour = "black", alpha = 0.9
  ) +
  ylim(-20,40)+
  xlim(-2.8,6)+
  theme_minimal() +
  theme(legend.position = "none")+
  geom_line(aes(x= invLNPC2, y= ref4), data=trend4)  +
  xlab("Aridity & Radiation (-PC2)")  +
  ylab ("NIR (res) reflectivity (%)")


grid.arrange(PVS, PVL, PNS, PNL, nrow = 2)

```


# Conclusions
<br>
For Visible reflectivity the interaction between Size and PC1 was signifficant.
Lower PC1 = higher humidity (vapour, rain and clouds) lower aridity. 
Smaller beetles reflect more visible light in humid environments

<br>
For NIR reflectivity the interaction between Size and PC2 was signifficant. 
Lower PC2 = higher solar radiation, higher max temp, more days above 35 and more aridity
Smaller beetles reflect less NIR light in hot/arid environments.