---
title: Polarisation analysis without outliers
author: Laura Ospina-Rozo
editor_options: 
  chunk_output_type: console
---

We repeated the analysis for degree of polarisation and the raw RGB value sin the right handed polarisation filter excluding the outliers: A. prasinus and the species belonging to the genus Xylonichus, Paraschizognathus because, unlike many scarabs, these species are known to have a bilayered mechanism that is not chiral. 

# Setting up

## Libraries

Libraries sourced from an additional script.

```{r message = FALSE, warning=FALSE}
source(here::here("Scripts/MacroEcol_1_Libraries.R"))
```

## Data sets

Import polarisation data.

```{r}
# elytra
PolBySpp <- read.csv(here::here("Data/FromCode/PolarzElytraBySpp.csv"))[-1] %>% 
  dplyr::arrange(phylogeny_name) %>%
  dplyr::filter(
    !str_detect(phylogeny_name, "Xylonichus_sp"),
    !str_detect(phylogeny_name, "Anoplognathus_prasinus"),
    !str_detect(phylogeny_name, "Paraschizognathus_ocularis"),
    !str_detect(phylogeny_name, "Paraschizognathus_prasinus"),
    !str_detect(phylogeny_name, "Paraschizognathus_olivaceous")
  )

PolByInd <- read.csv(here::here("Data/FromCode/PolarzElytraByInd.csv"))[-1] %>% 
  dplyr::filter(
    !str_detect(ind, "xyls"),
    !str_detect(ind, "prsi"),
    !str_detect(ind, "xyle"),
    !str_detect(ind, "pczo"),
    !str_detect(ind, "pczp"),
    !str_detect(ind, "pczv")
  )


# elytra and pronotum
#BeetlePol <- read.csv(here::here("Data/FromCode/PolarzElytraPronot.csv"))[-1]


```

All statistical analysis were done at the species level (polarisation data by species). Plots are produced with the polarisation data by individual.

And we imported the phylogeny from a .nwk file which contains 2000 phylogenetic trees. This allows us to test our hypothesis in multiple trees and not only on the MCC tree. This way, we account for any uncertainty in unresolved tips of our phylogeny.

```{r}
# Phylogeny
trees <- ape::read.tree(here::here("Data/XMAS_mat2b_bst2ef_set23nn2_pinct.nwk"))

# Set subset limits
trees_subset_min<-1000
trees_subset_max<-2000

MCCtree <- 
  ape::read.nexus(here::here("Data/xmas_mat2b_bst2ef_set23nn2_pinct_med.tre"))
```

To explore the correlations between ecological variables and polarisation

```{r}
# PC Values
PCValuesF <- read.csv(here::here("Data/FromCode/PCsbySpp.csv"))[-1] %>% 
  dplyr::rename("PC1" = PC1_1, "PC2" = PC2_1) %>% 
  dplyr::arrange(phylogeny_name) %>%
  dplyr::filter(
    !str_detect(phylogeny_name, "Xylonichus_sp"),
    !str_detect(phylogeny_name, "Anoplognathus_prasinus"),
    !str_detect(phylogeny_name, "Paraschizognathus_ocularis"),
    !str_detect(phylogeny_name, "Paraschizognathus_prasinus"),
    !str_detect(phylogeny_name, "Paraschizognathus_olivaceous")
  )

# merge with polarisation
PolPCs <- merge(PCValuesF, PolBySpp)

# adapt to merge with phylogeny
PolPCs2 <- as.data.frame(PolPCs) # create new data frame
rownames(PolPCs2) <- PolPCs2[, 1] # make species the row names
PolPCsRows <- PolPCs2[, 2:length(PolPCs2)] # eliminate spp name (redundant)
```

To explore correlations with reflectivity

```{r}
# Reflectivity data consolidated by species
ReflBySpp <- read.csv(here::here("Data/FromCode/ConsolidatedReflectivitySpp.csv"))[-1] %>% 
  dplyr::arrange(phylogeny_name) %>% 
  dplyr::filter(
    !str_detect(phylogeny_name, "Xylonichus_sp"),
    !str_detect(phylogeny_name, "Anoplognathus_prasinus"),
    !str_detect(phylogeny_name, "Paraschizognathus_ocularis"),
    !str_detect(phylogeny_name, "Paraschizognathus_prasinus"),
    !str_detect(phylogeny_name, "Paraschizognathus_olivaceous")
  )

# Merge with polarisation
PolRefl <- merge(ReflBySpp, PolBySpp)

# adapt to merge with phylogeny
PolRefl2 <- as.data.frame(PolRefl) # create new data frame
rownames(PolRefl2) <- PolRefl2[, 1] # make species the row names
PolReflRows <- PolRefl2[, 2:length(PolRefl2)] # eliminate spp name (redundant)
```

To explore correlations with absorptivity

```{r}
AbsBySpp <- read.csv(here::here("Data/FromCode/ConsolidatedAbsorptivitySpp.csv"))[-1] %>%
  dplyr::arrange(phylogeny_name) %>%
  dplyr::filter(
    !str_detect(phylogeny_name, "Xylonichus_sp"),
    !str_detect(phylogeny_name, "Anoplognathus_prasinus"),
    !str_detect(phylogeny_name, "Paraschizognathus_ocularis"),
    !str_detect(phylogeny_name, "Paraschizognathus_prasinus"),
    !str_detect(phylogeny_name, "Paraschizognathus_olivaceous")
  )

# merge with polarisation
PolAbs <- merge(AbsBySpp, PolBySpp)

# adapt to merge with phylogeny
PolAbs2 <- as.data.frame(PolAbs) # create new data frame
rownames(PolAbs2) <- PolAbs2[, 1] # make species the row names
PolAbsRows <- PolAbs2[, 2:length(PolAbs2)] # eliminate spp name (redundant)


```


To explore correlations with reflectivity only in Right handed polarisation (as a proxy of the amount of melanin/pigments)

```{r}

# Import equalised values for right handed polarisation
RHand0<-read.csv(here::here("Data/FromCode/PolarzElytra_LERGBValues.csv"))[-1]%>% 
  dplyr::filter(Type == "RCP") %>% 
  dplyr::select(-Type) %>% 
  dplyr::mutate(spp= substr(ind,1,4)) %>% 
  dplyr::group_by(spp) %>% 
  dplyr::summarise(
    meanRCP = mean(RGB_ave),
    sdRCP = sd(RGB_ave),
    )

# Join them with the phylogeny names
SppNames<-read.csv(here::here("Data/9_CodesAndSpecies.csv")) %>% 
  dplyr::mutate("spp" = substr(Ind,1,4)) %>% 
  dplyr::select(-Ind) %>% 
  distinct()


RHand <- merge(RHand0[,c(1,2)],SppNames) %>% 
 dplyr::arrange(phylogeny_name) %>%
  dplyr::filter(
    !str_detect(phylogeny_name, "Xylonichus_sp"),
    !str_detect(phylogeny_name, "Anoplognathus_prasinus"),
    !str_detect(phylogeny_name, "Paraschizognathus_ocularis"),
    !str_detect(phylogeny_name, "Paraschizognathus_prasinus"),
    !str_detect(phylogeny_name, "Paraschizognathus_olivaceous")
  )

# Name the right hand RGB "pol" to use the accessory scripts for multiple trees:
RHand <- 
  RHand %>% 
  dplyr::rename(Pol = meanRCP) %>% 
  dplyr::group_by(phylogeny_name) %>% 
  dplyr::summarise(Pol= mean(Pol))


# Combine with reflectivity

RHandRefl <- merge(ReflBySpp, RHand) 

RHandRefl2 <- as.data.frame(RHandRefl) # create new data frame
rownames(RHandRefl2) <- RHandRefl2[, 1] # make species the row names
RHandReflRows <- RHandRefl2[, 2:length(RHandRefl2)] # eliminate spp name 



# Combine with absorptivity

RHandAbs <- merge(AbsBySpp, RHand) 

RHandAbs2 <- as.data.frame(RHandAbs) # create new data frame
rownames(RHandAbs2) <- RHandAbs2[, 1] # make species the row names
RHandAbsRows <- RHandAbs2[, 2:length(RHandAbs2)] # eliminate spp name 


```



We prune the species in the tree that are not present in the dataset

```{r}

# Prune extra spp in the tree, not contain in the test sample
PolAbs.species.MCC <- as.data.frame(unique(PolAbs2$phylogeny_name))
PolRefl.species.MCC <- as.data.frame(unique(PolRefl2$phylogeny_name))


# Convert to "row names" (required for following steps)
row.names(PolAbs.species.MCC) <- PolAbs.species.MCC[, 1] 
row.names(PolRefl.species.MCC) <- PolRefl.species.MCC[, 1] 

# Make sure the names in data set and tree match
PolAbs.temp.MCC <- name.check(MCCtree, PolAbs.species.MCC)
PolRefl.temp.MCC <- name.check(MCCtree, PolRefl.species.MCC)

# This step is necessary because the tips are different.
MCCtreeAbs <- drop.tip(MCCtree, PolAbs.temp.MCC$tree_not_data)
MCCtreeRefl <- drop.tip(MCCtree, PolRefl.temp.MCC$tree_not_data)

# Test if the species are the same
identical(
  length(name.check(MCCtreeAbs, PolAbs2$phylogeny_name)$tree_not_data),
  length(PolAbs2$phylogeny_name)
)

identical(
  length(name.check(MCCtreeRefl, PolRefl2$phylogeny_name)$tree_not_data),
  length(PolRefl2$phylogeny_name)
)

```


# Optical properties

## Pol Degree

This is an indication of "how much of the colour is circularly polarised to the left". As a simplification, we assume that this is equivalent to most of the reflections produced by a chiral mechanism

### Reflectivity

#### VIS

<p style="color: #04C799">

**Question**

</p>

**Can polarisation predict visible reflectivity?**

<p style="color: #04C799">

**Correlation**

</p>

```{r}
cor.test(PolRefl$VIS, PolRefl$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL1 <- lm(PolRefl$VIS ~ PolRefl$Pol) # by spp
summary(ModL1)
```

<p style="color: #04C799">

**PGLS**

</p>

Create the data frame of comparative data

```{r}

comp_data <- comparative.data(
  phy = MCCtreeRefl,
  data = PolRefl, # aggregated data without the spp in the row names
  names.col = "phylogeny_name", # contains the column phylogeny name
  vcv = TRUE,
  na.omit = FALSE, warn.dropped = TRUE
)
```

Establish the model

```{r message= FALSE, warnings=FALSE}
pglsPDVIS <- pgls(VIS ~ Pol,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDVIS)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Function

Note that the function has to be modified for the predictors and data frame that we are using

```{r warning=FALSE, message=FALSE}
source(here::here("Scripts/6_multiple_pgls_function_A.R")) # script A is for Polarization as a response
```

Model

```{r}
MuPGLSPol3 <- Response ~ Pol
```

Dataset

```{r message=FALSE}

PolRefl3 <-
    PolReflRows %>% # phylogeny names in rows
    dplyr::select(Pol, VIS) %>% 
    dplyr::rename("Response" = VIS)

PolRefl3 <- as.data.frame(PolRefl3)
```

Apply

```{r message=FALSE, warning=FALSE}
runsPol3 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runA, model = MuPGLSPol3, dataset = PolRefl3)

dfPol3 <- ldply(runsPol3, data.frame)

length(dfPol3[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfPol3))
```

[ **Conclusion** ]{style="color: #04C799"} <br/>

**There's no correlation between visible reflectivity and polarisation at the species level.**

<br> <br> <br>

#### NIR

<p style="color: #04C799">

**Question**

</p>

**Is polarisation correlated with NIR reflectivity?**

<p style="color: #04C799">

**Correlation**

</p>

Species level:

```{r}
cor.test(PolRefl$NIR, PolRefl$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL2 <- lm(PolRefl$NIR ~ PolRefl$Pol + PolRefl$VIS) # by spp
summary(ModL2)
```

<p style="color: #04C799">

**PGLS**

</p>

The data frame of comparative data is the same as for visible light

```{r message= FALSE, warnings=FALSE}
pglsPDNIR <- pgls(NIR ~ Pol + VIS,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDNIR)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Function

Note that the function has to be modified for the predictors and data frame that we are using

```{r warning=FALSE, message=FALSE}
source(here::here("Scripts/13_multiple_pgls_function_H.R")) # script H is for Polarization as a predictor
```

Model

```{r}
MuPGLSPol4 <- Response ~ Pol + VIS
```

Dataset

```{r message=FALSE}

PolRefl4 <-
    PolReflRows %>% # phylogeny names in rows
    dplyr::select(Pol, VIS, NIR) %>% 
    dplyr::rename("Response" = NIR)

PolRefl4 <- as.data.frame(PolRefl4)
length(PolRefl4$Pol)
```

Apply

```{r message=FALSE, warning=FALSE}
runsPol4 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runH, model = MuPGLSPol4, dataset = PolRefl4)

dfPol4 <- ldply(runsPol4, data.frame)

length(dfPol4[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfPol4))
```

#### FRS

<p style="color: #04C799">

**Question**

</p>

**Is polarisation correlated with the NIR residuals corrected by phylogeny?**

<p style="color: #04C799">

**Correlation**

</p>

Species level:

```{r}
cor.test(PolRefl$FRS, PolRefl$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL3 <- lm(PolRefl$FRS ~ PolRefl$Pol) # by spp
summary(ModL3)
```

<p style="color: #04C799">

**PGLS**

</p>

The data frame of comparative data is the same as for visible light

```{r message= FALSE, warnings=FALSE}
pglsPDFRS <- pgls(FRS ~ Pol,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDFRS)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Dataset

```{r message=FALSE}

PolRefl5 <-
    PolReflRows %>% # phylogeny names in rows
    dplyr::select(Pol, FRS) %>% 
    dplyr::rename("Response" = FRS)

PolRefl5 <- as.data.frame(PolRefl5)
```

Apply

```{r message=FALSE, warning=FALSE}
runsPol5 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runA, model = MuPGLSPol3, dataset = PolRefl5)

dfPol5 <- ldply(runsPol5, data.frame)

length(dfPol5[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfPol5))
```

### Absorptivity

#### VIS

<p style="color: #04C799">

**Question**

</p>

**Can polarisation predict visible absorptivity?**

<p style="color: #04C799">

**Correlation**

</p>

```{r}
cor.test(PolAbs$VIS, PolAbs$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL1Abs <- lm(PolAbs$VIS ~ PolAbs$Pol) # by spp
summary(ModL1Abs)
```

<p style="color: #04C799">

**PGLS**

</p>

Create the data frame of comparative data

```{r}

CompDataAbs <- comparative.data(
  phy = MCCtreeAbs,
  data = PolAbs, # aggregated data without the spp in the row names
  names.col = "phylogeny_name", # contains the column phylogeny name
  vcv = TRUE,
  na.omit = FALSE, warn.dropped = TRUE
)
```

Establish the model

```{r message= FALSE, warnings=FALSE}
pglsPDVISAbs <- pgls(VIS ~ Pol,
  data = CompDataAbs, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDVISAbs)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Dataset

```{r message=FALSE}

PolAbs3 <-
    PolAbsRows %>% # phylogeny names in rows
    dplyr::select(Pol, VIS) %>% 
    dplyr::rename("Response" = VIS)

PolAbs3 <- as.data.frame(PolAbs3)
```

Apply

```{r message=FALSE, warning=FALSE}
runsPol6 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runA, model = MuPGLSPol3, dataset = PolAbs3)

dfPol6 <- ldply(runsPol6, data.frame)

length(dfPol6[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfPol6))
```

[ **Conclusion** ]{style="color: #04C799"} <br/>

**There's no correlation between visible absorptivity and polarisation at the species level.**

<br> <br> <br>

#### NIR

<p style="color: #04C799">

**Question**

</p>

**Is polarisation correlated with NIR absorptivity?**

<p style="color: #04C799">

**Correlation**

</p>

Species level:

```{r}
cor.test(PolAbs$NIR, PolAbs$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL2Abs <- lm(PolAbs$NIR ~ PolAbs$Pol + PolAbs$VIS) # by spp
summary(ModL2Abs)
```

<p style="color: #04C799">

**PGLS**

</p>

The data frame of comparative data is the same as for visible light

```{r message= FALSE, warnings=FALSE}
pglsPDNIRAbs <- pgls(NIR ~ Pol + VIS,
  data = CompDataAbs, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDNIRAbs)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Dataset

```{r message=FALSE}

PolAbs4 <-
    PolAbsRows %>% # phylogeny names in rows
    dplyr::select(Pol, VIS, NIR) %>% 
    dplyr::rename("Response" = NIR)

PolAbs4 <- as.data.frame(PolAbs4)
```

Apply

```{r message=FALSE, warning=FALSE}
runsPol7 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runH, model = MuPGLSPol4, dataset = PolAbs4)

dfPol7 <- ldply(runsPol7, data.frame)

length(dfPol7[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfPol7))
```

#### FRS

<p style="color: #04C799">

**Question**

</p>

**Is polarisation correlated with the NIR residuals corrected by phylogeny?**

<p style="color: #04C799">

**Correlation**

</p>

Species level:

```{r}
cor.test(PolAbs$FRS, PolAbs$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL3Abs <- lm(PolAbs$FRS ~ PolAbs$Pol) # by spp
summary(ModL3Abs)
```

<p style="color: #04C799">

**PGLS**

</p>

The data frame of comparative data is the same as for visible light

```{r message= FALSE, warnings=FALSE}
pglsPDFRSAbs <- pgls(FRS ~ Pol,
  data = CompDataAbs, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDFRSAbs)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Dataset

```{r message=FALSE}

PolAbs5 <-
    PolAbsRows %>% # phylogeny names in rows
    dplyr::select(Pol, FRS) %>% 
    dplyr::rename("Response" = FRS)

PolAbs5 <- as.data.frame(PolAbs5)
```

Apply

```{r message=FALSE, warning=FALSE}
runsPol8 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runA, model = MuPGLSPol3, dataset = PolAbs5)

dfPol8 <- ldply(runsPol8, data.frame)

length(dfPol8[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfPol8))
```




## Right handed Pol



### Reflectivity

#### VIS

<p style="color: #04C799">

**Question**

</p>

**Can the darkness in the underlaying pigment affect the visible reflectivity?**

<p style="color: #04C799">

**Correlation**

</p>

```{r}
cor.test(RHandRefl$VIS, RHandRefl$Pol) # by spp

```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL1RH <- lm(RHandRefl$VIS ~ RHandRefl$Pol) # by spp
summary(ModL1RH)
```

<p style="color: #04C799">

**PGLS**

</p>

Create the data frame of comparative data

```{r}

comp_dataRH <- comparative.data(
  phy = MCCtreeRefl,
  data = RHandRefl, # aggregated data without the spp in the row names
  names.col = "phylogeny_name", # contains the column phylogeny name
  vcv = TRUE,
  na.omit = FALSE, warn.dropped = TRUE
)
```

Establish the model

```{r message= FALSE, warnings=FALSE}
pglsPDVISRH <- pgls(VIS ~ Pol,
  data = comp_dataRH, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDVISRH)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Function

Note that the function has to be modified for the predictors and data frame that we are using

```{r warning=FALSE, message=FALSE}
source(here::here("Scripts/6_multiple_pgls_function_A.R")) # script A is for Polarization as a response
```

Model

```{r}
MuPGLSPol3 <- Response ~ Pol
```

Dataset

```{r message=FALSE}

RHandRefl3 <-
    RHandReflRows %>% # phylogeny names in rows
    dplyr::select(Pol, VIS) %>% 
    dplyr::rename("Response" = VIS)

RHandRefl3 <- as.data.frame(RHandRefl3)
```

Apply

```{r message=FALSE, warning=FALSE}
runsRHPol3 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runA, model = MuPGLSPol3, dataset = RHandRefl3)

dfRHPol3 <- ldply(runsRHPol3, data.frame)

length(dfRHPol3[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfRHPol3))
```

[ **Conclusion** ]{style="color: #04C799"} <br/>

**PENDING.**

<br> <br> <br>

#### NIR

<p style="color: #04C799">

**Question**

</p>

**Can the darkness in the underlaying pigment affect the NIR reflectivity?**

<p style="color: #04C799">

**Correlation**

</p>

Species level:

```{r}
cor.test(RHandRefl$NIR, RHandRefl$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL2RH <- lm(RHandRefl$NIR ~ RHandRefl$Pol + RHandRefl$VIS) # by spp
summary(ModL2RH)
```

<p style="color: #04C799">

**PGLS**

</p>

The data frame of comparative data is the same as for visible light

```{r message= FALSE, warnings=FALSE}
pglsPDNIRRH <- pgls(NIR ~ Pol + VIS,
  data = comp_dataRH, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDNIRRH)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Function

Note that the function has to be modified for the predictors and data frame that we are using

```{r warning=FALSE, message=FALSE}
source(here::here("Scripts/13_multiple_pgls_function_H.R")) # script A is for Polarization as a response
```

Model

```{r}
MuPGLSPol4 <- Response ~ Pol + VIS
```

Dataset

```{r message=FALSE}

RHandRefl4 <-
    RHandReflRows %>% # phylogeny names in rows
    dplyr::select(Pol, VIS, NIR) %>% 
    dplyr::rename("Response" = NIR)

RHandRefl4 <- as.data.frame(RHandRefl4)
```

Apply

```{r message=FALSE, warning=FALSE}
runsRHPol4 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runH, model = MuPGLSPol4, dataset = RHandRefl4)

dfRHPol4 <- ldply(runsRHPol4, data.frame)

length(dfRHPol4[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfRHPol4))
```

#### FRS

<p style="color: #04C799">

**Question**

</p>

**Can the darkness in the underlaying pigment affect the NIR reflectivity?**

<p style="color: #04C799">

**Correlation**

</p>

Species level:

```{r}
cor.test(RHandRefl$FRS, RHandRefl$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL3RH <- lm(RHandRefl$FRS ~ RHandRefl$Pol) # by spp
summary(ModL3RH)
```

<p style="color: #04C799">

**PGLS**

</p>

The data frame of comparative data is the same as for visible light

```{r message= FALSE, warnings=FALSE}
pglsPDFRSRH <- pgls(FRS ~ Pol,
  data = comp_dataRH, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDFRSRH)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Dataset

```{r message=FALSE}

RHandRefl5 <-
    RHandReflRows %>% # phylogeny names in rows
    dplyr::select(Pol, FRS) %>% 
    dplyr::rename("Response" = FRS)

RHandRefl5 <- as.data.frame(RHandRefl5)
```

Apply

```{r message=FALSE, warning=FALSE}
runsRHPol5 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runA, model = MuPGLSPol3, dataset = RHandRefl5)

dfRHPol5 <- ldply(runsRHPol5, data.frame)

length(dfRHPol5[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfRHPol5))
```

### Absorptivity

#### VIS

<p style="color: #04C799">

**Question**

</p>

**Can polarisation predict visible absorptivity?**

<p style="color: #04C799">

**Correlation**

</p>

```{r}
cor.test(RHandAbs$VIS, RHandAbs$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL1AbsRH <- lm(RHandAbs$VIS ~ RHandAbs$Pol) # by spp
summary(ModL1AbsRH)
```

<p style="color: #04C799">

**PGLS**

</p>

Create the data frame of comparative data

```{r}

CompDataAbsRH <- comparative.data(
  phy = MCCtreeAbs,
  data = RHandAbs, # aggregated data without the spp in the row names
  names.col = "phylogeny_name", # contains the column phylogeny name
  vcv = TRUE,
  na.omit = FALSE, warn.dropped = TRUE
)
```

Establish the model

```{r message= FALSE, warnings=FALSE}
pglsPDVISAbsRH <- pgls(VIS ~ Pol,
  data = CompDataAbsRH, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDVISAbsRH)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Dataset

```{r message=FALSE}

RHandAbs3 <-
    RHandAbsRows %>% # phylogeny names in rows
    dplyr::select(Pol, VIS) %>% 
    dplyr::rename("Response" = VIS)

RHandAbs3 <- as.data.frame(RHandAbs3)
```

Apply

```{r message=FALSE, warning=FALSE}
runsRHPol6 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runA, model = MuPGLSPol3, dataset = RHandAbs3)

dfRHPol6 <- ldply(runsRHPol6, data.frame)

length(dfRHPol6[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfRHPol6))
```

[ **Conclusion** ]{style="color: #04C799"} <br/>

**There's no correlation between visible absorptivity and polarisation at the species level.**

<br> <br> <br>

#### NIR

<p style="color: #04C799">

**Question**

</p>

**Is polarisation correlated with NIR absorptivity?**

<p style="color: #04C799">

**Correlation**

</p>

Species level:

```{r}
cor.test(RHandAbs$NIR, RHandAbs$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL2AbsRH <- lm(RHandAbs$NIR ~ RHandAbs$Pol + RHandAbs$VIS) # by spp
summary(ModL2AbsRH)
```

<p style="color: #04C799">

**PGLS**

</p>

The data frame of comparative data is the same as for visible light

```{r message= FALSE, warnings=FALSE}
pglsPDNIRAbsRH <- pgls(NIR ~ Pol + VIS,
  data = CompDataAbsRH, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDNIRAbsRH)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Dataset

```{r message=FALSE}

RHandAbs4 <-
    RHandAbsRows %>% # phylogeny names in rows
    dplyr::select(Pol, VIS, NIR) %>% 
    dplyr::rename("Response" = NIR)

RHandAbs4 <- as.data.frame(RHandAbs4)
```

Apply

```{r message=FALSE, warning=FALSE}
runsRHPol7 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runH, model = MuPGLSPol4, dataset = RHandAbs4)

dfRHPol7 <- ldply(runsRHPol7, data.frame)

length(dfRHPol7[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfRHPol7))
```

#### FRS

<p style="color: #04C799">

**Question**

</p>

**Is polarisation correlated with the NIR residuals corrected by phylogeny?**

<p style="color: #04C799">

**Correlation**

</p>

Species level:

```{r}
cor.test(RHandAbs$FRS, RHandAbs$Pol) # by spp
```

<p style="color: #04C799">

**Linear model**

</p>

```{r}
ModL3AbsRH <- lm(RHandAbs$FRS ~ RHandAbs$Pol) # by spp
summary(ModL3AbsRH)
```

<p style="color: #04C799">

**PGLS**

</p>

The data frame of comparative data is the same as for visible light

```{r message= FALSE, warnings=FALSE}
pglsPDFRSAbsRH <- pgls(FRS ~ Pol,
  data = CompDataAbsRH, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDFRSAbsRH)
```

<p style="color: #04C799">

**PGLS multiple trees**

</p>

Dataset

```{r message=FALSE}

RHandAbs5 <-
    RHandAbsRows %>% # phylogeny names in rows
    dplyr::select(Pol, FRS) %>% 
    dplyr::rename("Response" = FRS)

RHandAbs5 <- as.data.frame(RHandAbs5)
```

Apply

```{r message=FALSE, warning=FALSE}
runsRHPol8 <- lapply(trees[trees_subset_min:trees_subset_max],
                   pgls_runA, model = MuPGLSPol3, dataset = RHandAbs5)

dfRHPol8 <- ldply(runsRHPol8, data.frame)

length(dfRHPol8[,1])
```

Get results

```{r}
HPDinterval(as.mcmc(dfRHPol8))
```


