---
title: "Calculating degree of polarisation"
# author: "Laura Ospina-Rozo"
# date: "25/04/2022"
editor_options: 
  chunk_output_type: console
---

<br>
<br>

We calculated the reflectance of the beetles from the RGB values measured from calibrated photographs to find the degree of circular polarization.

First we linearised the RBGs using the parameters derived from the MATLAB code adapted from Stevens et al 2007 (Biological Journal of the Linnean society, 90(2), 211-237). Next we equalised the RGB values with the grey standard with known reflectance. Finally, we calculated the difference between the two polarizations standardized by their sum.

<br>

In the second part of this script, we correlate the polarization with reflectivity obtained in previous scripts

<br>
<br>

# Setting up

## General

Libraries sourced from an additional script

```{r message = FALSE, warning=FALSE}
source(here::here("Scripts/MacroEcol_1_Libraries.R"))
```

We included an overall option to keep as many decimals as possible in our data, which is important for our calculations

```{r}
options(scipen = 100)
```

We imported the data set containing ecological and phylogeny data obtained in previous steps. 

```{r}
Cons1 <- read.csv(here::here("Data/FromCode/ConsReflEcolInd.csv"))[-1]
```


## Parameters

To calibrate, we photographed a set of 2%, 20%, 40%, 60%, 80% and 99% and standards. Then, we fitted a polynomial regression between the RGB values the standards display in our set up and their expected reflectance on each channel (obtained from the manufacturer), using a custom made function in MatLab. 

Since the pictures were not taken on the same day, we calibrated the beetle photographs to the photographs of the standards taken on the same day. That means we had one set of parameters for each camera configuration (in the code this is called camera_cat)

The parameters obtained from these curves were stored in .txt files, so we wrote a function to import them directly.

```{r}

read_parameters_from_file <- function(camera_cat, type) {
  param <- read.table(paste0(
    here::here("Data/ParametersMatLab/StandardParams"),
    camera_cat, type, ".txt"
  ), header = TRUE) %>%
    dplyr::select(1:5, 7) %>%
    dplyr::mutate(camera_cat = rep(camera_cat)) %>%
    dplyr::mutate(type = rep(type))

  return(param)
}

parameter0 <-
  bind_rows(
    read_parameters_from_file("J21", "LCP"),
    read_parameters_from_file("J21", "RCP"),
    read_parameters_from_file("J21", "VIS"),
    read_parameters_from_file("J25", "LCP"),
    read_parameters_from_file("J25", "RCP"),
    read_parameters_from_file("J25", "VIS"),
    read_parameters_from_file("J26", "LCP"),
    read_parameters_from_file("J26", "RCP"),
    read_parameters_from_file("J26", "VIS"),
    read_parameters_from_file("F01", "LCP"),
    read_parameters_from_file("F01", "RCP"),
    read_parameters_from_file("F01", "VIS"),
    read_parameters_from_file("F04", "LCP"),
    read_parameters_from_file("F04", "RCP"),
    read_parameters_from_file("F04", "VIS")
  )
```

The regression uses 4 parameters a, b, c, and d. We obtained one value for each parameter, on each channel (R,G, B) for each type of filter (VIS = Visible, LCP =left handed circularly polarized and RCP= right circularly polarized) on each camera configuration (camera_cat)

```{r}

parameter <-
  parameter0 %>% dplyr::filter(Channel != "Gy") %>% # keep only the channels R, G, B.
  dplyr::select(-5) %>% # this column is the % of fitting (ideally) above 0.99)
  gather(
    key = parameter,
    value = value,
    -Channel, -type, -camera_cat
  ) # re-arrange: All parameters in 1 column

head(parameter)
```

## Grey Standard

This is the known reflectance (from manufacturer) of the 40% grey placed next to each beetle in the photographs

```{r}

grey_standard_refl <- read.csv(here::here("Data/12_knownGreyStdReflectance.csv"))
```

## Raw RGB values

These are the RGB valuyes extracted from the calibrated photographs. We considered one region of interest (ROI) in one elytron and one in the pronotum. We also sampled the 40% grey as a reference.

```{r import data, echo = FALSE, message = FALSE}
RGB_raw <- read.csv(here::here("Data/10_Polarization.csv"))

# simplify
RGB_raw_transform <-
  RGB_raw %>%
  # remove these columns that we do not need:
  dplyr::select(-Pic_code, -ANIC, -SpeciesName, -area, -min, -max) %>%
  # Change names
  dplyr::rename(
    "type" = Filter, # This means VIS, Left polarize, or right polarized
    "Channel" = label, # This means R, G or B
    "value" = mean
  ) %>% # This refers to the value of each channel
  dplyr::filter(ind != "pind03") # removed because values were repeated accidentally
```


**Elytra**

We separated the RGB values of the elytra and the grey standard but kept a unique identifier called PhotoID. This helps pairing the sample with the grey that was in that picture further in the analysis (required to run the linearisation function).

```{r}

RGBElytraNGrey <-
  RGB_raw_transform %>%
  dplyr::filter(tr != "Pronotum") %>% # remove data for the pronotum
  unite("PhotoID", # Create a unique code
    c(1, 2, 4), # which contains the individual_Filter_Channel
    remove = FALSE
  ) # still keep all the original columns

# Each beetle sample has a grey standard in the same photo.
levels(as.factor(RGBElytraNGrey$tr))

# We will separate the elytra and grey
# but they will still share the unique PhotoID to pair them later

RGBElytra <-
  RGBElytraNGrey %>%
  dplyr::filter(tr == "Elytra")

RGBElGrey <-
  RGBElytraNGrey %>%
  dplyr::filter(tr == "Grey")
```



**Pronotum**

Pronotum data was not available for the following beetles: 

```{r}

RGBPronot1 <-
  RGB_raw_transform %>%
  dplyr::filter(tr != "Elytra") %>% # remove data for the elytra
  unite("PhotoID", # Create a unique code
    c(1, 2, 4), # which contains the individual_Filter_Channel
    remove = FALSE
  ) # still keep all the original columns

inPGind <- levels(as.factor(RGBPronot1[RGBPronot1$tr == "Grey", ]$ind))
inPRind <- levels(as.factor(RGBPronot1[RGBPronot1$tr == "Pronotum", ]$ind))

setdiff(inPGind, inPRind)
setdiff(inPRind, inPGind)
# Note pronotum missing for these: "ecry03" "mcla02" "roci02"
```

They are considered for the overall polarization analysis but not in the correlations elytra-pronotum.

We separated the RGB values of the pronotum and the grey standard but kept a unique identifier called PhotoID. This helps pairing the sample with the grey that was in that picture further in the analysis (required to run the linearisation function).

```{r}

RGBPronot1 <-
  RGBPronot1 %>%
  dplyr::filter(ind != "ecry03" &
    ind != "mcla02" &
    ind != "roci02") # Remove these species because pronotum unavailable

RGBPronot <-
  RGBPronot1 %>%
  dplyr::filter(tr == "Pronotum")

RGBPrGrey <-
  RGBPronot1 %>%
  dplyr::filter(tr == "Grey")
```




# Calibrations

Here we linearise and equalise RGBs for each camera setting and each channel separately.

First we defined the functions as follows: 
<br>

<span style="color: #04C799"> **Linearization** </span>  <br/>

$$\ Y = a*exp(b*x) + c*exp(d*x)$$
Where a, b c and d are the parameters obtained from MatLab. x is the raw RGB value for the ROI and Y is the linearised value


```{r}

# The arguments of this functions are:
# a DataFrame: containing the RGB values that we want to linearise
# a ParameterData: a data frame containing the parameters a,b,c,d from MatLab

lin_equ_RGB <- function(DataFrame, ParameterData) {
  Result <- DataFrame # keep the original data, results will be added to it
  Result$Linearized <- rep("NA", length(DataFrame[1])) # add an empty column

  for (i in 1:length(DataFrame$PhotoID)) {
    para <- ParameterData %>% # the data frame with the parameters

      # For each line in the DataFrame to linearise, we need to find
      # the correspondent set of parameters:
      dplyr::filter(type == DataFrame$type[i], # VIS, LCP, or RCP
        Channel == DataFrame$Channel[i], # R, G or B
        camera_cat == DataFrame$camera_cat[i]) %>% # Camera conditions
      dplyr::arrange(., parameter) # arranged alphabetically

    # Apply the formula
    Result$Linearized[i] <-
      para$value[1] * exp(para$value[2] * Result$value[i]) +
      para$value[3] * exp(para$value[4] * Result$value[i])
  }
  return(Result)
}
```


<span style="color: #04C799"> **Equalisation** </span>  <br/>

$$\ E = l / (rg /(kg*255))$$
Where rg is the raw RGB values for the grey in the photo, kg is the known reflectance of the gray standard (from the fabricator), l is the linearised value of the ROI and E is the equalised value of the ROI.


For this part we did not use and equation, rather we obtained the calculations directly form the data frames.

## Elytra

#### Linearise

We applied the function defined in the previous step

```{r}

LinearizedElytra <- lin_equ_RGB(RGBElytra, parameter) %>%
  dplyr::select(PhotoID, tr, Linearized) # apply function

head(LinearizedElytra)

LinearizedElytra$Linearized <- round(as.numeric
(LinearizedElytra$Linearized), 4) # round

LinearizedElytraSpr <-
  LinearizedElytra %>%
  spread(tr, Linearized)
```

#### Equalise

And then equalised following the equation

```{r}

RGBElGreys <-
  RGBElGrey %>%
  dplyr::select(PhotoID, value) # select the relevant columns of the raw grey values

EQElytra <-
  merge(RGBElGreys, LinearizedElytraSpr,
    all = FALSE
  ) %>%
  dplyr::rename(RawGrey = value) %>%
  dplyr::mutate(
    Equalized =
      Elytra / (RawGrey / (grey_standard_refl[1, 2] * 255))
  )
```


#### Average 

We averaged the RGB values of the three channels for each filter.

```{r}

RGB_ave <- EQElytra %>%
  dplyr::select(PhotoID, Equalized) %>%
  dplyr::mutate(Reflectance = Equalized * 100) %>%
  dplyr::select(-Equalized) %>%
  separate(PhotoID, c("ind", "Type", "Channel"), sep = "_") %>%
  dplyr::group_by(ind, Type) %>%
  dplyr::mutate(RGB_ave = mean(Reflectance)) %>%
  dplyr::select(ind, Type, RGB_ave) %>%
  dplyr::distinct() %>% # leave only the one row for each individual
  dplyr::filter(!grepl("ambl", ind)) %>%
  dplyr::filter(!grepl("sqzb", ind)) # remove, absent in the phylogeny

head(RGB_ave)
```


## Pronotum

#### Linearise

We applied the function defined in the previous step

```{r}
LinearizedPron <- lin_equ_RGB(RGBPronot, parameter) %>%
  select(PhotoID, tr, Linearized) # apply function

head(LinearizedPron)

LinearizedPron$Linearized <- round(as.numeric
(LinearizedPron$Linearized), 4) # round

LinearizedPronSpr <-
  LinearizedPron %>%
  spread(tr, Linearized)
```

#### Equalise

And then equalised following the equation

```{r}

RGBPrGreys <-
  RGBPrGrey %>%
  dplyr::select(PhotoID, value) # select the relevant columns of the raw grey values

EQPronot <-
  merge(RGBPrGreys, LinearizedPronSpr,
    all = FALSE
  ) %>%
  dplyr::rename(RawGrey = value) %>%
  dplyr::mutate(
    Equalized =
      Pronotum / (RawGrey / (grey_standard_refl[1, 2] * 255))
  )
```


#### Average

We averaged the RGB values of the three channels for each filter.

```{r}

RGB_avePr <- EQPronot %>%
  dplyr::select(PhotoID, Equalized) %>%
  dplyr::mutate(Reflectance = Equalized * 100) %>%
  dplyr::select(-Equalized) %>%
  separate(PhotoID, c("ind", "Type", "Channel"), sep = "_") %>%
  dplyr::group_by(ind, Type) %>%
  dplyr::mutate(RGB_aveP = mean(Reflectance)) %>%
  dplyr::select(ind, Type, RGB_aveP) %>%
  dplyr::distinct() %>% # leave only the one row for each individual
  dplyr::filter(!grepl("ambl", ind)) %>%
  dplyr::filter(!grepl("sqzb", ind)) # remove, absent in the phylogeny

head(RGB_avePr)
```



# Polarization

We calculated the polarization as $$\ P \ = \frac{l - r}{l + r}$$

where $l$ represents the mean reflectance under the filter for left handed circular polarization and $r$ represents the mean reflectance under the filter for right handed circular polarization.


## Elytra

First export data frame with the Raw polarisation values in case it is needed
```{r}

write.csv(RGB_ave, here::here("Data/FromCode/PolarzElytra_LERGBValues.csv"))

```


Thus we obtained the polarization values for the elytron ROI by individual and by species:

```{r}

# Calculate the polarization:
ElyPol <-
  RGB_ave %>%
  spread(Type, RGB_ave) %>%
  dplyr::mutate(Polarization = (LCP - RCP) / (LCP + RCP))

head(ElyPol) # by individual

# To find the mean value per spp: 

ElyPolbb <-
  ElyPol %>%
  dplyr::select(ind, Polarization) %>%
  dplyr::mutate(spp = substr(ind, 1, 4)) # Add column for spp

ElyPolbb <-  as.data.frame(ElyPolbb)

# Import species names
SppNames <- read.csv(here::here("Data/9_CodesAndSpecies.csv"))

SppNames <-
  SppNames %>% 
  mutate (spp = substr(Ind, 1, 4)) %>% 
  filter (spp != "ambl"& # Amblyterus cicatricosus
          spp != "psqz"& # Pseudoschizongnatus schoenfeldti
          spp != "saul"& # Saulostomus villosus
          spp != "sqzb"& # Schizognathus burmeisteri
          spp != "sqzc"& # Schizognathus compressicornis
          spp != "sqzm"  # Schizognathus mesosternalis
            ) %>% # These species were removed. No phylogenetic info
  dplyr::select (-spp) %>% 
  dplyr::arrange(Ind) %>% 
  dplyr::rename("ind" = Ind)

# Combine the two data frames
ElyPolbyindN <- merge(ElyPolbb, SppNames, by="ind") # merge as "inner join"

# mean by species
EPolbs <-
  ElyPolbyindN%>%
  select(Polarization, phylogeny_name) %>% 
  dplyr::group_by(phylogeny_name) %>%
  dplyr::summarise(Pol = mean(Polarization)) # by species

```


## Pronotum

Thus we obtained the polarization values for the pronotum ROI by individual:

```{r}
# Calculate the polarization:
ProPol <-
  RGB_avePr %>%
  spread(Type, RGB_aveP) %>%
  dplyr::mutate(Polarization = (LCP - RCP) / (LCP + RCP))

head(ProPol) #  by individual
```

And by species:

```{r}

# Average: One polarization value by spp
ProPolbysp <-
  ProPol %>%
  dplyr::select(ind, Polarization) %>%
  dplyr::mutate(spp = substr(ind, 1, 4)) # Add column for spp

PPolbs <-
  ProPolbysp[2:3] %>%
  dplyr::group_by(spp) %>%
  dplyr::summarise(Pol = mean(Polarization)) # by species

head(PPolbs)
```


## Combined 

Join the two data frames of polarisation by elytra and pronotum.

First make sure the two data frames contain the same number of species, thus the differences between the individuals in both data frames should be 0


```{r}
ProPol <-
  ProPol %>%
  dplyr::rename(PronotPol = Polarization)

ElyPol <-
  ElyPol %>%
  dplyr::rename(ElytrPol = Polarization) # Keep all spp for other tests


ElyPolEP <-
  ElyPol %>%
  filter(ind != "ecry03" &
    ind != "mcla02" &
    ind != "roci02") # Removed, pronotum unavailable

inelytra <- levels(as.factor(ElyPolEP$ind))
inpronotum <- levels(as.factor(ProPol$ind))

setdiff(inelytra, inpronotum)
setdiff(inpronotum, inelytra)
```

Merge

```{r}

# simplify Data frames
Elysimple <-
  ElyPolEP %>%
  select(ind, ElytrPol)

Prosimple <-
  ProPol %>%
  select(ind, PronotPol)

BeetlePol <-
  merge(Elysimple, Prosimple) %>% # Combine the two data frames
  dplyr::mutate(Difference = ElytrPol - PronotPol)

head(BeetlePol)

```







###################### REMOVE ############################################


Ecological variables

We merged the polarization data with the data frames obtained in previous steps that contain ecological variables, reflectivity, size and the species name as follows: 


First compare the dimensions of the two data frames (Reflectance and polarization):

```{r}

Cons1 <-
  Cons1 %>%
  mutate(spp = substr(ind, 1, 4))

inTree <- levels(as.factor(Cons1$spp))
inRGB <- levels(as.factor(EPolbs$spp))

setdiff(inTree, inRGB)
setdiff(inRGB, inTree)
```

Both contain the same species

```{r}

# Compare length:
length(Cons1$ind)
length(ElyPol$ind)

# subset the consolidated by the ind in polariz data frame
Refbyind <- Cons1[Cons1$ind %in% ElyPol$ind, ]
```

But since they had different numbers of individuals we only considered the ones that were common for both data frames to combine them into one larger data frame

```{r}
# Simplify the polarization data
ElyPolbyind <-
  ElyPol %>%
  select(1, 5) # keep only one column and the individual

RPData <-
  merge(Refbyind, ElyPolbyind) # Combine the two

head(RPData)
```

We also summarised this data by species 

```{r}
RPDataAgg <-
  RPData %>%
  dplyr::select(-ind, -spp) %>% # remove individual id
  dplyr::select(phylogeny_name, everything()) %>% # order columns
  dplyr::group_by(phylogeny_name) %>% # group
  dplyr::summarise(across(everything(), list(mean))) # mean

head(RPDataAgg)
```

This way we can conduct the analysis at both individual and species level

<br>
<br>

# Results from this step

As a general conclusion it does seem that there can be three mechanisms: White underlay, chiral and broadband chiral. 


We obtained a data frame useful to compare the degree of polarization between two body parts, elytron and pronotum

```{r}
write.csv(BeetlePol, here::here("Data/FromCode/PolarzElytraPronot.csv"))
```


We also obtained data frames with the degree of polarisation by individual and by species: 

```{r}

write.csv(ElyPolbyindN, here::here("Data/FromCode/PolarzElytraByInd.csv")) # by individual
write.csv(EPolbs, here::here("Data/FromCode/PolarzElytraBySpp.csv")) # by species

```


