---
title: "Polarisation PGLS"
# author: "Laura Ospina-Rozo"
---

In this script we study the Polarization trait corrected by phylogeny. 

# Setting up

Libraries sourced from an additional script

```{r message = FALSE, warning=FALSE}
source("./MacroEcol_1_Libraries.R")
```

We imported the data obtained from previous steps.

We first aggregated the polarization and environment data to get one value per species for each variable

```{r}

RPDataAgg <- read.csv("../Data/FromCode/PolarzElytraRefl.csv")[-1]
head(RPDataAgg)

RPDAgg1 <-
  RPDataAgg %>%
  dplyr::select(-ind, -spp) %>%
  dplyr::select(phylogeny_name, everything()) %>%
  dplyr::group_by(phylogeny_name) %>% # group
  dplyr::summarise(across(everything(), list(mean))) # mean

# Convert to a data frame for the comparative.data function
RPDAgg1 <- as.data.frame(RPDAgg1)
head(RPDAgg1)
names(RPDAgg1) <- c(
  "phylogeny_name",
  "TOT", "VIS", "NIR", "Res", "size",
  "PC1", "PC2", "Pol"
)
# Modify to make it compatible with tree tips
RPDAgg <- as.data.frame(RPDAgg1) # create new data frame
rownames(RPDAgg) <- RPDAgg[, 1] # make species the row names
RPDAgg <- RPDAgg[, 2:length(RPDAgg)] # eliminate spp name (redundant)
```

We separated it into different data frames which is useful for plotting

```{r}
names(RPDAgg) <- c(
  "TOT", "VIS", "NIR", "Res", "size",
  "PC1", "PC2", "Pol"
)

TOTdf <- RPDAgg %>% dplyr::select(TOT)
VISdf <- RPDAgg %>% dplyr::select(VIS)
NIRdf <- RPDAgg %>% dplyr::select(NIR)
Resdf <- RPDAgg %>% dplyr::select(Res)
PC1df <- RPDAgg %>% dplyr::select(PC1)
PC2df <- RPDAgg %>% dplyr::select(PC2)
Sizdf <- RPDAgg %>% dplyr::select(size)
Poldf <- RPDAgg %>% dplyr::select(Pol)
```

And we imported the phylogeny from a .nwk file which contains 2000 phylogenetic trees. This allows us to test our hypothesis in multiple trees and not only on the MCC tree. This way, we account for any uncertainty in unresolved tips of our phylogeny.

```{r}

# Phylogeny
trees <- ape::read.tree("../Data/XMAS_mat2b_bst2ef_set23nn2_pinct.nwk")
```

We created the subsets we need to test our hypothesis


```{r}

PDVIS <-
  RPDAgg %>%
  dplyr::select(-TOT, -NIR, -Res) %>%
  dplyr::rename("Reflectance" = VIS) # keep only visible reflectivity

PDPol <-
  RPDAgg %>%
  dplyr::select(-TOT, -NIR, -Res, -VIS) %>%
  dplyr::rename("Polarization" = Pol) # keep only polarization
```



# Plot in Tree

<span style="color: #04C799"> **Question** </span>  <br/>

Chiral structures are supposed to be well conserved within scarabs. Thus, abscense or low polarization should be unusual and perhaps clustered in only a few branches of the phylogenetic tree.  

**Does the degree of polarization cluster according to phylogeny?**

```{r warning = FALSE}

# read the tree
MCCtree.raw <-
  ape::read.nexus("../Data/xmas_mat2b_bst2ef_set23nn2_pinct_med.tre")

# Prune extra spp in the tree, not contain in the test sample
species.MCC <- as.data.frame(unique(RPDataAgg$phylogeny_name))

# Convert to "row names" (required for following steps)
row.names(species.MCC) <- species.MCC[, 1]

# Make sure the names in data set and tree match
temp.MCC <- name.check(MCCtree.raw, species.MCC)

# This step would be neccesary if the tips had been different.
# MCCtree <- drop.tip(MCCtree.raw, temp.MCC$tree_not_data)

# Instead, changed the name
MCCtree <- MCCtree.raw

# create phylogeny object for ggtree()
phylo.MCC <- ggtree(MCCtree, layout = "rectangular") + geom_tiplab(size = 1.5)

# set xlim
phylo.MCC + xlim(0, 25) +
  geom_nodepoint(col = "gold", alpha = 0.4)
```

Plot the traits on the tree

The values that we include in this plot has to be the average between individuals, since there is only one branch per species.


```{r eval=FALSE}

# create a MCC tree without tip names for the plot
tree_only <- ggtree(MCCtree, layout = "rectangular")

# create heat map columns
# Note: log transforms increase contrast for visualization purposes

# Add Polariz
p0 <- gheatmap(tree_only, Poldf,
  width = 0.05, low = "gray90", high = "black",
  font.size = 2,
  colnames_position = "bottom", colnames_angle = 0,
  colnames_offset_x = 0, colnames_offset_y = -0.5,
  legend_title = "Pol"
)
```


```{r eval=FALSE}

# Add Reflectance

# VIS
p3.scale <- p0 + new_scale_fill() # add new scale for second variable
p3 <- gheatmap(p3.scale, log(VISdf),
  offset = 1.5, # to avoid overlapping with p1
  width = 0.05, low = "#1b9e77", high = "#FFFFBF",
  font.size = 2,
  colnames_position = "bottom", colnames_angle = 0,
  colnames_offset_x = 0, colnames_offset_y = -0.5,
  legend_title = "VIS"
)

# NIR
p4.scale <- p3 + new_scale_fill() # add new scale for second variable
p4 <- gheatmap(p4.scale,
  log(
    NIRdf + # get log to bring them closer to each other
      (abs((min(NIRdf))) + 1) # make them all positive
  ), # this correction allows better visualization
  offset = 3,
  width = 0.05, low = "#88419d", high = "#edf8fb",
  font.size = 2,
  colnames_position = "bottom", colnames_angle = 0,
  colnames_offset_x = 0, colnames_offset_y = -0.5,
  legend_title = "NIR"
)

p4
```

# Questions

## Phylogeny

<span style="color: #04C799"> **Question** </span>  <br/>

**Do visible reflectivity and polarization evolve separately?**

If the two evolve together their correlation should dissapear when after applying the phylogenetic correction and the phylogenetic signal in these traits would be high

<span style="color: #04C799"> **Tests** </span>  <br/>

### PGLS in the MCC

Create the data frame of comparative data

```{r}

comp_data <- comparative.data(
  phy = MCCtree,
  data = RPDAgg1, # aggregated data without the spp in the row names
  names.col = "phylogeny_name", # contains the column phylogeny name
  vcv = TRUE,
  na.omit = FALSE, warn.dropped = TRUE
)
```

Establish the model

```{r message= FALSE, warnings=FALSE}
pglsPDVIS <- pgls(VIS ~ Pol,
  data = comp_data, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDVIS)
```

Test phylogenetic signal using Pagel's lambda:

Phylogenetic signal is high in VIS reflectivity.

```{r}

pagelPDVIS <- PDVIS$Reflectance # Define which trait you want to test
names(pagelPDVIS) <- rownames(PDVIS) # Row names = tree tips
phylosig(MCCtree, pagelPDVIS, method = "lambda", test = TRUE, nsim = 999)
# nsim = 999 means testing with 999 randomizations
```

Phylogenetic signal is high for Polarization.

```{r}

pagelPDPol <- PDVIS$Pol # Define which trait you want to test
names(pagelPDPol) <- rownames(PDVIS) # Row names = tree tips
phylosig(MCCtree, pagelPDPol, method = "lambda", test = TRUE, nsim = 999)
# nsim = 999 means testing with 999 randomizations
```



<span style="color: #04C799"> **Conclusion** </span>  <br/>

**High visible reflectivity and polarization did not evolve independently. They do cluster according to phylogeny.**

<br>
<br>
<br>


### PGLS in multiple trees


Function

Note that the function has to be modified for the predictors and data frame that we are using

```{r warning=FALSE, message=FALSE}
source("6_multiple_pgls_function_A.R") # script A is for Polarization as predictor
```

Model

```{r }

MuPGLSPol1 <- Reflectance ~ Pol
```

Dataset

```{r message=FALSE}
# Add the phylogeny name again because in this function it is needed:
PDVIS2 <-
  PDVIS %>%
  dplyr::mutate(phylogeny_name = rownames(PDVIS)) %>%
  dplyr::select(Reflectance, Pol)

PDVIS2 <- as.data.frame(PDVIS2)
head(PDVIS2)
```

Apply

```{r message=FALSE, warning=FALSE}
runsPol1 <- lapply(trees, pgls_runA, model = MuPGLSPol1, dataset = PDVIS2)

dfPol1 <- ldply(runsPol1, data.frame)
```

Get results
```{r}
HPDinterval(as.mcmc(dfPol1))
```




## Ecology

<span style="color: #04C799"> **Question** </span>  <br/>

**Is polarization correlated to the extracted climate variables?**


### PGLS in the MCC

Create the data frame of comparative data

```{r}

comp_data2 <- comparative.data(
  phy = MCCtree,
  data = RPDAgg1, # aggregated data without the spp in the row names
  names.col = "phylogeny_name", # contains the column phylogeny name
  vcv = TRUE,
  na.omit = FALSE, warn.dropped = TRUE
)

head(RPDAgg1)
```

Establish the model

```{r message= FALSE, warnings=FALSE}

pglsPDPol <- pgls(Pol ~ PC1 + PC2 + size + PC1 * size + PC2 * size,
  data = comp_data2, param.CI = 0.95, lambda = "ML"
)

summary(pglsPDPol)
```

Polarization

```{r}

pagelPDPol <- PDVIS$Pol # Define which trait you want to test
names(pagelPDPol) <- rownames(PDVIS) # Row names = tree tips
phylosig(MCCtree, pagelPDPol, method = "lambda", test = TRUE, nsim = 999)
# nsim = 999 means testing with 999 randomizations
```

Phylogenetic signal is high. 

<span style="color: #04C799"> **Conclusion** </span>  <br/>

**Polarization does not directly correlate with these ecological variables**

<br>
<br>
<br>


### PGLS in multiple trees


Function

Note that the function has to be modified for the predictors and data frame that we are using

```{r warning=FALSE, message=FALSE}
source("7_multiple_pgls_function_B.R") # script A is for Polarization as a response
```

Model

```{r }
MuPGLSPol2 <- Polarization ~ PC1 + PC2 + size + PC1 * size + PC2 * size
```

Dataset

```{r message=FALSE}
# Add the phylogeny name again because in this function it is needed:
PDPol2 <-
  PDPol %>%
  dplyr::mutate(phylogeny_name = rownames(PDPol)) %>%
  dplyr::select(phylogeny_name, Polarization, size, PC1, PC2)

PDPol2 <- as.data.frame(PDPol2)
```

Apply

```{r message=FALSE, warning=FALSE}
runsPol2 <- lapply(trees, pgls_runB, model = MuPGLSPol2, dataset = PDPol2)

dfPol2 <- ldply(runsPol2, data.frame)
```

Get results
```{r}
HPDinterval(as.mcmc(dfPol2))
```




# Conclusions

* Polarization is indeed a well preserved character in this group of beetles. 
* The degree of polarization does not correlate with any of the studied ecological variables.
* However, some beetles may use their chiral structures to reflect more visible light. These beetles tend to have more polarization and higher visible reflectivity.

